---
title: "N4S human wellbeing data generation"
output:
  html_document: default
  word_document:
  pdf_document: default
---
**Background**

This script generates for all available N4S datasets, human wellbeing (HWB) variables at the household level for
material, subjective and relational dimensions.

I first set up a dataframe with all of the potential variables, then add the 
variables for each dataset. Each dataset has different formats so I load and
generate variables seperately for each project.

For each variables I note the description of the new variable generated, and print
the underyling codes of the original variables before any recoding. Refer to the
relevant survey form and documentation for the original question and codes.

**1. R Setup**
```{r setup,  message = FALSE, warning = FALSE}

#### a) check packages and install if needed ###################################
check.packages <- function(pkg){
      new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
      if (length(new.pkg))
          install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  }
check.packages(c("ggplot2","knitr","xlsx","Hmisc","BBmisc","dplyr","grid",
                 "reshape2","tidyr","car","openxlsx"))

#### b) R markdown and knitr stuff ###################################
knitr::opts_chunk$set(echo = TRUE) ; knitr::opts_chunk$set(root.dir = getwd())

# require
require(readr)
require(dplyr)
require(tidyr)
```

**2. Load functions**
```{r functions, message = FALSE, warning = FALSE}

#### a) get general functions ###################################
source('functions.R')

# function to view variables as levels
lvls <- function(dt){apply(dt[-1],2,function(x)levels(factor(x)))}

```

**3. Set up main dataframe**
```{r dataframe, message = FALSE, warning = FALSE}

#### a) set up dataframe to which to append variables from each dataset #######

hwb_all <- data.frame(stringsAsFactors = F,
  
  ## ID VARIABLES AND DEMOGRAPHICS
  pjnm = as.character(), # project name
  cn = character(), # country
  yr = numeric(), # year covered by survey (latest year, where period is over several years)
  admn1 = character(), # admin division 1 (e.g. one below national)
  admn2 = character(), # admin division 2
  admn3 = character(), # admin division 3
  admn4 = character(), # admin division 4 (e.g. village; ward)
  admn1n = character(), # admin division number codes
  admn2n = character(), 
  admn3n = character(), 
  admn4n = character(), 
  ses = character(), # social-ecological zone
  pj_hhid = character(), # id for household used in project
  gnd = character(), # respondent gender
  rsp_age = as.numeric(), # respondent age
  
  ## MATERIAL WELLBEING INDICATORS
  # See here for full details of the variables for each dataset:
  # https://docs.google.com/spreadsheets/d/1TqLXVJ0kDP8ugOtzmwDj1LciyPkcLjujTZioRkhqvCs/edit?usp=sharing
  # i) EDUCATION
  edu_yrs = as.numeric(), # years of schooling
  edu_chld_att = as.numeric(), # child school attendance
  # ii) HEALTH
  hlt_chld_mt = as.numeric(), # child mortality
  hlt_fd_sec = as.numeric(), # food security
  hlt_pt = as.numeric(), # protein consumption
  # iii) LIVING STANDARDS
  ls_elec = as.numeric(), # electricity
  ls_san = as.numeric(), # sanitation
  ls_wat = as.numeric(), # drinking water
  ls_hse = as.numeric(), # housing
  ls_fuel = as.numeric(), # cooking fuel
  ls_ast = as.numeric(), # valuable assets
  # iii) LIVELIHOODS
  lv_pas = as.numeric(), # productive assets
  # v) RISK
  rk_exp = as.numeric(), # exposure to risk
  
  ## SUBJECTIVE WELLBEING INDICATOR
  # see here for details: https://docs.google.com/document/d/1fN_6p05nBirVFrkw0GwDSRH1d6CVBb_Bl3a7BpIWkDA/edit#bookmark=id.9riqvl5i7glt
  swb = character(),
  
  ## RELATIONAL WELLBEING INDICATOR
  # see here for details: https://docs.google.com/document/d/1fN_6p05nBirVFrkw0GwDSRH1d6CVBb_Bl3a7BpIWkDA/edit#bookmark=id.xorp28w1m05x
  
  rwb_cm_st = as.numeric(), # community opportunity structures
  rwb_cm_ag = as.numeric(), # community agency
  rwb_fm_st = as.numeric(), # family opportunity structures
  rwb_fm_ag = as.numeric() # familty agency
  
)

# keep df col order
dford <- names(hwb_all)


```

**4. SPACES**
```{r spaces, message = FALSE, warning = FALSE}

#### a) get data from SQL database and add to spaces list  #####################
spaces <- list() # empty list
# load data and add raw data tables to spaces list
sp_db <- RSQLite::dbConnect(RSQLite::SQLite(), dbname="../data/raw/spaces_initial/hhsurvey_database.sqlite")
tbl <- RSQLite::dbListTables(sp_db) # list tables
tbl <- tbl[!grepl("sqlite_",tbl)] # remove unneeded sql files
for (i in seq(along=tbl)) { # loop to extract tables and add to list
  spaces[[i]] <- RSQLite::dbGetQuery(conn=sp_db, 
                                     statement=paste("SELECT * FROM '", tbl[[i]], "'", sep=""))
  spaces[[i]][spaces[[i]]==-9] <- NA # convert NAs
  names(spaces)[i] <- tbl[i]
}
# get survye ids linked to hh heads
RSQLite::dbDisconnect(sp_db) # disconnect db

# check commonality of gear
# tmp <-full_join(spaces$cover,spaces$t07_12fish_gear,by="survid") %>%
#   select(site,gear,habitat) %>%
#   drop_na() %>%
#   unite("gear_habitat", gear:habitat,remove = F) %>%
#   distinct() %>%
#   group_by(habitat) %>%
#   tally()

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS
hwb_tmp <- data.frame(stringsAsFactors = F,
  pj_hhid = as.character(spaces$cover$hhid),
  survid = spaces$cover$survid, # add survid for joining, remove later
  yr = 2014,
  pjnm = rep("sp",nrow(spaces$cover)),
  cn = spaces$cover$country,
  admn1 = NA, # to add from spatial data
  admn2 = NA, # to add from spatial data
  admn3 = NA, # to add from spatial data
  admn4 = spaces$cover$site, # village
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = NA,
  ses = NA, # to add
  gnd = spaces$cover$gender,
  rsp_age = spaces$cover$age
)
hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("female","male"))) # add names to gender
hwb_tmp$cn[hwb_tmp$cn=="kenya"] <- "KEN" # align country names
hwb_tmp$cn[hwb_tmp$cn=="mz"] <- "MOZ"
hwb_tmp$admn4 <- as.character(factor(hwb_tmp$admn4,labels=c( # align village names
  "Kongowea", "Lalane", "Maringanha", "Mieze", "Mkwiro", "Tzunza", "vamizi", "Vanga" 
)))

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- spaces$t05census %>%
  dplyr::select(survid,age,edu) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  group_by(survid) %>%
  summarise(edu_yrs = ifelse(length(age[edu>=6]>=10)>0,1,0)) %>%  # ifelse recode
  full_join(hwb_tmp,.)
  # codes
  lvls(vrs)

# edu_chld_att
# Any school-aged child is not attending school for at least six years
hwb_tmp <- spaces$t05census %>%
  dplyr::select(survid,age,edu) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  group_by(survid) %>%
  summarise(edu_chld_att = ifelse(length(age[edu<4]<=18)>0,0,1)) %>% # ifelse recode
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)


## HEALTH

# hlt_chld_mt
# Chronic illness in household in last year
hwb_tmp <- spaces$t03need_ke %>% # kenya
  dplyr::select(survid,hlt_chld_mt_ke = q351) %>%
  drop_na() %>%
  #mutate(hlt_chld_mt=ifelse(hlt_chld_mt==1,0,1)) %>%
  full_join(hwb_tmp,.)
hwb_tmp <- spaces$t03need_mz %>% # kenya
  dplyr::select(survid,hlt_chld_mt_mz = q351) %>%
  drop_na() %>%
  #mutate(hlt_chld_mt=ifelse(hlt_chld_mt==1,0,1)) %>%
  full_join(hwb_tmp,.) %>%
  mutate(hlt_chld_mt = dplyr::coalesce(hlt_chld_mt_ke, hlt_chld_mt_mz)) %>%
  dplyr::select(-hlt_chld_mt_ke, -hlt_chld_mt_mz)
  #mutate(hlt_chld_mt=replace(hlt_chld_mt,is.na(hlt_chld_mt),1))

# hlt_fd_sec
# Reported not having enough to eat in the last 12 months
hwb_tmp <- spaces$t03need_ke %>% # kenya
  dplyr::select(survid,hlt_fd_sec = q341) %>% # use raw variable
  drop_na() %>%
  full_join(hwb_tmp,.)
hwb_tmp <- spaces$t03need_mz %>% # mozambique
  dplyr::select(survid,hlt_fd_sec = q341) %>% # use raw variable
  drop_na() %>%
  right_join(hwb_tmp, by= "survid") %>%
  mutate(hlt_fd_sec = dplyr::coalesce(hlt_fd_sec.x, hlt_fd_sec.y)) %>%
  dplyr::select(-c(hlt_fd_sec.x, hlt_fd_sec.y)) %>%
  { . ->> vrs } # keep vars
 # codes
  lvls(vrs[c(1,ncol(vrs))])


# hlt_pt
# Did not eat meat in last week, or every week on average over period
# first need to convert reported dates to days before survey
hwb_tmp <- spaces$t10food %>% # kenya
  dplyr::select(survid,q1033) %>% # use raw variable
  right_join(spaces$cover[c("survid","hhid" ,"date")], by= "survid") %>% # add date of survey
  mutate(date = ifelse(substr(date,1,2) %in% c(12,13), # fix survey date format 
                       paste(substr(date,7,8),substr(date,4,5),"14",sep="/"),
                       paste(substr(date,1,6),"14",sep=""))) %>%
  mutate(date = ifelse(substr(date,4,5) %in% c(13:31),
                       paste(substr(date,4,5),substr(date,1,2),"14",sep="/"),
                       date)) %>%
  group_by(hhid) %>%
  mutate(q1033 = getmode(q1033[!is.na(q1033)])) %>%
  ungroup() %>%
  drop_na(q1033) %>%
  mutate(date = as.Date(date,"%d/%m/%y")) %>% # convert date of survey
  mutate(ptd = as.numeric(date - as.Date(q1033,"%d/%m/%Y"))) %>% # get days since protien
  mutate(ptd = dplyr::coalesce(as.character(ptd),q1033)) %>% # merge with other data
  { . ->> vrs } %>% # keep vars
  mutate(hlt_pt = as.numeric(factor(q1033))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(hlt_pt = ifelse(hlt_pt %in% c(3,7,11,12,13,14,15,16),1,0)) %>%
  dplyr::select(survid,hlt_pt) %>%
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs[c(1,ncol(vrs))])

## LIVING STANDARDS

# ls_elec
# The household has no electricity
hwb_tmp <- spaces$t11asset %>%
  dplyr::select(survid,ls_elec = elec) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_elec = ifelse(ls_elec==1,0,1)) %>% # ifelse recode
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)


# ls_san
# The household’s sanitation facility is not flush toilet or latrine, or ventilated improved pit or composting toilet
hwb_tmp <- spaces$t03need_ke %>% # kenya
  dplyr::select(survid,q321,q322) %>%
  drop_na(q321) %>%
  { . ->> vrs } %>% # keep vars
  mutate(q322 = as.numeric(factor(q322))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(ls_san = ifelse(q321==0,0,ifelse(q322 %in% c(6,8,14),1,0))) %>%
  dplyr::select(survid,ls_san) %>%
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)

hwb_tmp <- spaces$t03need_mz %>% # mozambique
  dplyr::select(survid,q321,q322) %>%
  drop_na(q321) %>%
  { . ->> vrs } %>% # keep vars
  mutate(q322 = as.numeric(factor(q322))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(ls_san = ifelse(q321==0,0,ifelse(q322 %in% c(2,4,5,7),1,0))) %>%
  dplyr::select(survid,ls_san) %>%
  right_join(hwb_tmp, by= "survid") %>%
  mutate(ls_san = dplyr::coalesce(ls_san.x, ls_san.y)) %>%
  dplyr::select(-c(ls_san.x, ls_san.y))
 # codes
  lvls(vrs)


# ls_wat
# Is not piped water, public tap, borehole or pump, protected well, protected spring or rainwater
hwb_tmp <- spaces$t03need_ke %>% # kenya
  dplyr::select(survid,q331) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(q331 = as.numeric(factor(q331))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(ls_wat = ifelse(q331 %in% c(2,3,7,12),1,0)) %>%
  dplyr::select(survid,ls_wat) %>%
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)


hwb_tmp <- spaces$t03need_mz %>% # mozambique
  dplyr::select(survid,q331) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(q331 = as.numeric(factor(q331))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(ls_wat = ifelse(q331 %in% c(7,8,9,2,10,11,4,13,14),1,0)) %>%
  dplyr::select(survid,ls_wat) %>%
  right_join(hwb_tmp, by= "survid") %>%
  mutate(ls_wat = dplyr::coalesce(ls_wat.x, ls_wat.y)) %>%
  dplyr::select(-c(ls_wat.x, ls_wat.y))
 # codes
  lvls(vrs)


# ls_hse
# At least one of the three housing materials for roof, walls and floor are inadequate: the floor is of natural materials and/or the roof and/or walls are of natural or rudimentary materials
hwb_tmp <- spaces$t11asset %>%
  dplyr::select(survid,wall,roof,floor) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(wall = as.numeric(factor(wall))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(wall = ifelse(wall %in% c(6,5,9,15,18,19,20,21),1,0)) %>%
  mutate(roof = as.numeric(factor(roof))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(roof = ifelse(roof %in% c(2,5,6,9,10,11,13),1,0)) %>%
  mutate(floor = as.numeric(factor(floor))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(floor = ifelse(floor %in% c(1,2),0,1)) %>%
  mutate(ls_hse = ifelse(rowSums(dplyr::select(.,wall,roof,floor),na.rm=T)<2,0,1)) %>% # generate index
  full_join(hwb_tmp,.) %>%
  dplyr::select(-c(wall,roof,floor))
 # codes
  lvls(vrs)


# ls_fuel
# The household cooks with dung or wood
hwb_tmp <- spaces$t11asset %>%
  dplyr::select(survid,ls_fuel=cook) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_fuel = as.numeric(factor(ls_fuel))) %>% # make factor, then numeric, then recode all to deal with 'others'
  mutate(ls_fuel = ifelse(ls_fuel %in% c(3:6),1,0)) %>%
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)


# ls_ast
# The household does not own more than one of the following items: radio, TV, telephone, bike, motorbike computer, or refrigerator (conditional on not owning a car or truck). Or similar assets in each survey.
hwb_tmp <- spaces$t11asset %>%
  # no vars fir telephone or computer
  dplyr::select(survid,rad=q1158,tv=q1153,bk=q1159,mbk=q11510,dhw=q11515,fdg=q1151)  %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_ast = ifelse(rowSums(dplyr::select(.,-survid),na.rm=T)==0,0,1)) %>% # generate index
  dplyr::select(survid,ls_ast) %>%
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)

## bespoke ls_ast and lv_pas variables for anamika
ad_extra_tmp <- hwb_tmp %>%
  select(survid:admn4n)

ad_extra_tmp <- spaces$t11asset %>%
  # no vars fir telephone or computer
  dplyr::select(survid,rad=q1158,tv=q1153,#bk=q1159,mbk=q11510,
                dhw=q11515,fdg=q1151)  %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_ast = ifelse(rowSums(dplyr::select(.,-survid),na.rm=T)==0,0,1)) %>% # generate index
  dplyr::select(survid,ls_ast) %>%
  full_join(ad_extra_tmp,.)
 # codes
  lvls(vrs)

ad_extra_dat <- spaces$t11asset %>%
  dplyr::select(survid,q11519:q11524) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(q11519=as.numeric(factor(q11519))-1) %>% # make all zero based numeric code
  mutate(lv_pas = ifelse(rowSums(dplyr::select(.,-survid),na.rm=T)>0,1,0)) %>%
  dplyr::select(survid,lv_pas) %>%
  full_join(ad_extra_tmp,.)
 # codes
  lvls(vrs)
summary(ad_extra_dat)
  
## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: agricultural land; fishing vessel; livestock
hwb_tmp <- spaces$t11asset %>%
  dplyr::select(survid,q11519:q11524) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(q11519=as.numeric(factor(q11519))-1) %>% # make all zero based numeric code
  mutate(lv_pas = ifelse(rowSums(dplyr::select(.,-survid),na.rm=T)>0,1,0)) %>%
  dplyr::select(survid,lv_pas) %>%
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)
  
## RISK
# rk_exp
# Experienced a shock in the last year
hwb_tmp <- spaces$t02vuln %>%
  dplyr::select(survid,lowhigh,year) %>%
  right_join(spaces$cover[c("survid","hhid")]) %>%
  group_by(hhid) %>%
  mutate(lowhigh = getmode(lowhigh[!is.na(lowhigh)])) %>%
  ungroup() %>%
  #drop_na() %>%
  { . ->> vrs } %>% # keep vars
  filter(survid %in% hwb_tmp$survid) %>% # filter to remove duplicates
  group_by(survid) %>%
  summarise(rk_exp = ifelse(c("high") %in% lowhigh,1,0)) %>% # ifelse recode
  dplyr::select(survid,rk_exp) %>%
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)


## SUBJECTIVE WELLBEING

hwb_tmp <- spaces$t01wb %>%
  dplyr::select(survid,swb=satisf) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(swb = as.character(factor(swb,labels=c("Very satisfied", # add labels and make character
                                   "Satisfied",
                                   "Dissatisfied",
                                   "Very dissatisfied")))) %>%
  full_join(hwb_tmp,.)
 # codes
  lvls(vrs)


## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
hwb_tmp <- spaces$t03need_ke %>% # kenya
  dplyr::select(survid,rwb_cm_st=q382) %>% # use raw variable
  mutate(rwb_cm_st=replace(rwb_cm_st,which(is.na(rwb_cm_st)),0)) %>% # assume NAs are 0
  drop_na() %>%
  full_join(hwb_tmp,.)
hwb_tmp <- spaces$t03need_mz %>% # mozambique
  dplyr::select(survid,rwb_cm_st=q382) %>% # use raw variable
  #drop_na() %>%
  right_join(hwb_tmp, by= "survid") %>%
  mutate(rwb_cm_st = dplyr::coalesce(rwb_cm_st.x, rwb_cm_st.y)) %>%
  { . ->> vrs } %>% # keep vars
  dplyr::select(-c(rwb_cm_st.x, rwb_cm_st.y))
 # codes
  lvls(vrs[c(1,ncol(vrs))])

# Community agency
# rwb_cm_ag
# Alternative 1: No one outside of family to turn to if household needs help
hwb_tmp <- spaces$t03need_ke %>% # kenya
  dplyr::select(survid,rwb_cm_ag=q392) %>% # use raw variable
  drop_na() %>%
  full_join(hwb_tmp,.)
hwb_tmp <- spaces$t03need_mz %>% # mozambique
  dplyr::select(survid,rwb_cm_ag=q392) %>% # use raw variable
  drop_na() %>%
  right_join(hwb_tmp, by= "survid") %>%
  mutate(rwb_cm_ag = dplyr::coalesce(rwb_cm_ag.x, rwb_cm_ag.y)) %>%
  dplyr::select(-c(rwb_cm_ag.x, rwb_cm_ag.y))  %>% 
  { . ->> vrs } # keep vars
 # codes
  lvls(vrs[c(1,ncol(vrs))])


# Family opportunity structures
# rwb_fm_st
# No close relatives in the village
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
#  Alternative 1: Almost never (or) below involed in family decisions
hwb_tmp <- spaces$t03need_ke %>% # kenya
  dplyr::select(survid,rwb_fm_ag=q3103) %>% # use raw variable
  drop_na() %>%
  full_join(hwb_tmp,.)
hwb_tmp <- spaces$t03need_mz %>% # mozambique
  dplyr::select(survid,rwb_fm_ag=q3103) %>% # use raw variable
  drop_na() %>%
  right_join(hwb_tmp, by= "survid") %>%
  mutate(rwb_fm_ag = dplyr::coalesce(rwb_fm_ag.x, rwb_fm_ag.y)) %>%
  dplyr::select(-c(rwb_fm_ag.x, rwb_fm_ag.y)) %>%
  mutate(rwb_fm_ag = ifelse(rwb_fm_ag==1,0,1)) %>%  # ifelse recode  
  { . ->> vrs } # keep vars
 # codes
  lvls(vrs[c(1,ncol(vrs))])


## c) Check variables and tidy  ###################################

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)]

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# SPACES did several interviews per household
# just keeping most complete response for now, then taking first row for ties, assuming it was hh head
hwb_tmp <- hwb_tmp %>%
  mutate(value = rowSums(is.na(.))) %>%
  group_by(pj_hhid)  %>%
  filter(value == min(value)) %>% # get most complete response
  filter(row_number()==1) %>% # then first row in group
  dplyr::select(-c("value"))

# align variable classes with main dataframe
# for (i in 1:ncol(hwb_tmp)){
#   class(hwb_tmp[,i]) <- class(hwb_all[,i])}

# check col classes before merge
sapply(hwb_tmp,class)

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(hwb_tmp,sp_db,i,tbl,spaces)


```

**5. DELTAS **
```{r deltas, message = FALSE, warning = FALSE}

#### a) get data from csvs for each round  #####################
# add id for each round and bind to one dataframe

## household survey round 1
# - Falgun to Jaishthoo. Spring and Summer. mid Feb to mid June
de_hh_r1_raw <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,
                     "../data/raw/sango/DELTAS/1-Spatial/07-ESPA_Deltas_1st_Round.csv")
de_hh_r1_raw$rnd <- paste(de_hh_r1_raw$IDNO,"r1",sep="")

## household survey round 2
# - Ashar to Ashwin. Monsoon and Autumn. Mid-June to Mid October.
de_hh_r2_raw <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,
                     "../data/raw/sango/DELTAS/1-Spatial/08-ESPA_Deltas_2nd_Round.csv")
de_hh_r2_raw$rnd <- paste(de_hh_r2_raw$IDNO,"r2",sep="")

## household survey round 3
# - Kartik to Magh. Dry season Winter. Mid-October to Mid February
de_hh_r3_raw <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,
                     "../data/raw/sango/DELTAS/1-Spatial/09-ESPA_Deltas_3rd_Round.csv")
de_hh_r3_raw$rnd <- paste(de_hh_r3_raw$IDNO,"r3",sep="")

## make big dataframe
de_hh <- rbind(de_hh_r1_raw,de_hh_r2_raw,de_hh_r3_raw)

## deal with NAs
de_hh[de_hh==96] <- NA

## clean workspace
rm(de_hh_r1_raw,de_hh_r2_raw,de_hh_r3_raw)

## keep segment info for merge at end
de_seg <- unique(de_hh[c("IDNO","UNION","MOUZA","SEGMENT")])

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS
hwb_tmp <- data.frame(stringsAsFactors = F,
  IDNO = de_hh$IDNO,
  rnd = de_hh$rnd, # get round var for now, remove later
  pjnm = "de",
  cn = "BGD",
  yr = 2015,
  admn1 = NA, # to add name from spatial data
  admn2 = NA, # to add name from spatial data
  admn3 = NA, # to add name from spatial data
  admn4 = NA, # to add name from spatial data
  admn1n = de_hh$DIVISION, # to add name from spatial data
  admn2n = de_hh$DISTRICT, # to add name from spatial data
  admn3n = de_hh$UNION, # to add name from spatial data
  # admn4n = de_hh$MOUZA,
  admn4n = paste(de_hh$CLUSTER,de_hh$ZONE,de_hh$DIVISION,de_hh$DISTRICT,
                 de_hh$UPAZILA,de_hh$UNION,de_hh$MOUZA,sep=""),
  ses = de_hh$ZONE, # to add name from spatial data
  gnd = de_hh$Q104_01,
  rsp_age = de_hh$Q105_01
)

hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("female","male"))) # add names to gender

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,starts_with("Q105"),starts_with("Q109")) %>%
  gather(v, value, Q105_01:Q109_30) %>% # reshape
  separate(v, c("var", "col")) %>%
  arrange(rnd) %>%
  spread(var, value) %>%
  drop_na() %>%
  mutate(age=Q105,edu=Q109) %>%
  { . ->> vrs } %>% # keep vars
  group_by(rnd) %>%
  summarise(edu_yrs = ifelse(length(age[edu>=6]>=10)>0,1,0)) %>% # ifelse recode
  dplyr::select(rnd,edu_yrs) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs[c(1,5,6)])

# edu_chld_att
# Any school-aged child is not attending school for at least six years
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,starts_with("Q105"),starts_with("Q109")) %>%
  gather(v, value, Q105_01:Q109_30) %>% # reshape
  separate(v, c("var", "col")) %>%
  arrange(rnd) %>%
  spread(var, value) %>%
  drop_na() %>%
  mutate(age=Q105,edu=Q109) %>%
  { . ->> vrs } %>% # keep vars
  group_by(rnd) %>%
  summarise(edu_chld_att = ifelse(length(age[edu<4]<=18)>0,0,1)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs[c(1,5,6)])

## HEALTH

# hlt_chld_mt
# Alternative 1:  has any child below 5 years died in the last year 
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,hlt_chld_mt=Q216) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  group_by(rnd) %>%
  mutate(hlt_chld_mt=ifelse(hlt_chld_mt==1,0,1))%>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)


# hlt_fd_sec
# HH is in lowest quantile of food diversity in last seven days
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,starts_with("Q1302")) %>%
  drop_na() %>%
  mutate(hlt_fd_sec = -rowSums(select(.,starts_with("Q1302_")),na.rm=T)) %>%
  mutate(hlt_fd_sec=as.numeric(cut(hlt_fd_sec,breaks=quantile(hlt_fd_sec)))) %>%
  mutate(hlt_fd_sec=ifelse(hlt_fd_sec==1,0,1)) %>%
  dplyr::select(rnd,hlt_fd_sec) %>%
  full_join(hwb_tmp,.)

# hlt_pt
# Did not eat meat in last week, or every week on average over period
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,starts_with("Q1302")) %>%
  dplyr::select(rnd,Q1302_26:Q1302_34)  %>%
  { . ->> vrs } %>% # keep vars
  mutate(hlt_pt = ifelse(2 %in% Q1302_26:Q1302_34,1,0)) %>%
  dplyr::select(rnd,hlt_pt) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)


## LIVING STANDARDS

# ls_elec
# A1: Main source of light is not electric mains
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,ls_elec = Q213) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_elec = ifelse(ls_elec %in% c(2),1,0)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)


# ls_san
# The household’s sanitation facility is not flush toilet or latrine, or ventilated improved pit or composting toilet
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,ls_san = Q203) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_san = ifelse(ls_san %in% c(1:7),1,0)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)


# ls_wat
# Is not piped water, public tap, borehole or pump, protected well, protected spring or rainwater
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,ls_wat = Q206) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_wat = ifelse(ls_wat %in% c(1:5,7),1,0)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)


# ls_hse
# At least one of the three housing materials for roof, walls and floor are inadequate: the floor is of natural materials and/or the roof and/or walls are of natural or rudimentary materials
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,Q210:Q212) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(
    fl = ifelse(Q210 %in% c(1),0,1),
    wl = ifelse(Q211 %in% c(5:7),0,1),
    rf = ifelse(Q212 %in% c(4,7),0,1)
  ) %>% mutate(ls_hse = ifelse(rowSums(dplyr::select(.,fl,wl,rf),na.rm=T)<2,0,1)) %>%
  dplyr::select(rnd,ls_hse) %>%
  full_join(hwb_tmp,.) 
# codes
lvls(vrs)


# ls_fuel
# The household cooks with dung or similar
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,ls_fuel = Q202) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_fuel = ifelse(ls_fuel %in% c(9:11),0,1)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)


# ls_ast
# The household does not own more than one of the following items: radio, TV, telephone, bike, motorbike computer, or refrigerator (conditional on not owning a car or truck). Or similar assets in each survey.
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,rad=Q209_24,tv=Q209_25,ph=Q209_26,tph=Q209_27,bk=Q209_34, # no computer var
         mbk=Q209_35,cr=Q209_36,cr2=Q209_37,fdg=Q209_28) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(vars(rad:fdg), funs(-. + max(.,na.rm=T))) %>% # make zero based, with 0 as absence
  mutate(ls_ast = ifelse(rowSums(dplyr::select(.,-rnd),na.rm=T)>1,1,0)) %>%
  dplyr::select(rnd,ls_ast) %>%
  full_join(hwb_tmp,.) 
# codes
lvls(vrs)

## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: agricultural land; fishing vessel; livestock

hwb_tmp <- de_hh %>%
  dplyr::select(rnd,Q9D01,Q209_13,Q209_14,starts_with("Q9B01_")) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(vars(Q209_13:Q9B01_96),list(~ -. + max(.,na.rm=T))) %>% # make all vars zero based
  mutate(lv_pas = ifelse(rowSums(dplyr::select(.,-rnd),na.rm=T)>0,1,0)) %>% # recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## RISK
# rk_exp
# Experienced two shocks in the last year
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,starts_with("Q1001_")) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(vars(Q1001_1:Q1001_96), funs(-. + max(.,na.rm=T))) %>% # make zero based, with 0 as absence
  mutate(rk_exp = ifelse(rowSums(dplyr::select(.,-rnd),na.rm=T)>1,0,1)) %>%
  dplyr::select(rnd,rk_exp) %>%
  full_join(hwb_tmp,.) 
# codes
lvls(vrs)


## SUBJECTIVE WELLBEING
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,swb=Q1501A) %>%
  { . ->> vrs }  %>% # keep vars
  mutate(swb=as.character(swb)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Alternative 1: Has successfully been granted community land by the local NRM institution
# rwb_cm_st
hwb_tmp$rwb_cm_st <- as.numeric(NA)
  
# Community agency
# rwb_cm_ag
# No data
hwb_tmp <- de_hh %>%
  dplyr::select(rnd,rwb_cm_ag=Q1101B) %>% # khas land
  { . ->> vrs } %>% # keep vars
  mutate_at(vars(rwb_cm_ag), funs(ifelse(.>=2,0,1))) %>% # make zero based, with 0 as absence
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# No data
hwb_tmp$rwb_fm_ag <- as.numeric(NA) # no data

## c) Check variables and tidy  ###################################

# DELTAS did three rounds. below converting to yearly values for now
# using median or presence/absence as appropriate

hwb_tmp$rnd <- NULL # remove round var
names(hwb_tmp)[names(hwb_tmp)=="IDNO"] <- "pj_hhid" # rename ID
hwb_tmp <- hwb_tmp[names(hwb_all)] # align col order with main df

hwb_tmp <- hwb_tmp %>%
  group_by(pj_hhid) %>%
  summarise(
    pjnm = as.character(getmode(pjnm)),
    cn = as.character(getmode(cn)),
    yr = getmode(yr),
    admn1 = as.character(getmode(admn1)),
    admn2 = as.character(getmode(admn2)),
    admn3 = as.character(getmode(admn3)),
    admn4 = as.character(getmode(admn4)),
    admn1n = as.character(getmode(admn1n)), # admin division number codes
    admn2n = as.character(getmode(admn2n)), 
    admn3n = as.character(getmode(admn3n)), 
    admn4n = as.character(getmode(admn4n)), 
    ses = as.character(getmode(ses)),
    gnd = as.character(getmode(gnd)),
    rsp_age = getmode(rsp_age),
    edu_yrs = trunc(median(edu_yrs,na.rm=T)), 
    edu_chld_att = trunc(median(edu_chld_att,na.rm=T)),
    hlt_chld_mt = trunc(median(hlt_chld_mt,na.rm=T)),
    hlt_fd_sec = trunc(median(hlt_fd_sec,na.rm=T)),
    hlt_pt = trunc(median(hlt_pt, na.rm=T)),
    ls_elec = trunc(median(ls_san, na.rm=T)),
    ls_san = trunc(median(ls_san, na.rm=T)),
    ls_wat = trunc(median(ls_wat, na.rm=T)),
    ls_hse = trunc(median(ls_hse, na.rm=T)),
    ls_fuel = trunc(median(ls_fuel, na.rm=T)),
    ls_ast = trunc(median(ls_ast, na.rm=T)),
    lv_pas =  trunc(median(ls_ast, na.rm=T)),
    rk_exp = min(rk_exp, na.rm=T),
    swb = as.character(getmode(swb)),
    rwb_cm_st = trunc(median(rwb_cm_st, na.rm=T)),
    rwb_cm_ag = trunc(median(rwb_cm_ag, na.rm=T)),
    rwb_fm_st = trunc(median(rwb_fm_st, na.rm=T)),
    rwb_fm_ag = trunc(median(rwb_fm_ag, na.rm=T))
  )
hwb_tmp$pj_hhid <- as.character(hwb_tmp$pj_hhid)

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# check col classes before merge
sapply(hwb_tmp,class)

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(de_hh,hwb_tmp)

```

**6. PAGES **
```{r pages, message = FALSE, warning = FALSE}

#### a) get all data csvs in list object  #####################
nm <- c(list.files("../data/raw/sango/P4GES/1-P4GES_HHS_CE/data",full.names=T),
        list.files("../data/raw/sango/P4GES/2-P4GES_AGR_WHP/data",full.names=T))
pa_hh <- list()
for (i in 1:length(nm)){
  pa_hh[[i]] <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nm[i])
  names(pa_hh)[i] <- strsplit(nm[i],"/")[[1]][8]
  names(pa_hh)[i] <- substr(names(pa_hh)[i],1,nchar(names(pa_hh)[i])-15)
  pa_hh[[i]][pa_hh[[i]]==-98] <- NA # convert NAs
}

tmp <- pa_hh$HHS_S09_ASSET

tmp <- pa_hh$WHP_S02_PRODSHARV

# check how many village report harvests from rivers
# table(pa_hh$WHP_S02_PRODSHARV$fonkotany,
#       pa_hh$WHP_S02_PRODSHARV$prod_prior_name,
#       pa_hh$WHP_S02_PRODSHARV$imp_lvh)
# unique(pa_hh$WHP_S02_PRODSHARV$prod_prior_name)

# check prevalence of aquaculture
# names(pa_hh$AGR_S04_LIVESTOCK) # no ponds reported in ag survey
# table(pa_hh$HHS_S09_ASSET$fokontany, # only 3 out of
#       pa_hh$HHS_S09_ASSET$num_fish_tank)

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS
hwb_tmp <- data.frame(stringsAsFactors = F,
  resp_id = pa_hh$HHS_S01_INFO$resp_id,
  pjnm = "pa",
  cn = as.character("MDG"),
  yr = 2014,
  admn1 = as.character(NA), # to add name from spatial data
  admn2 = as.character(NA), # to add name from spatial data
  admn3 = as.character(NA), # to add name from spatial data
  admn4 = pa_hh$HHS_S01_INFO$fokontany,
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = NA, 
  ses = as.character(NA), # to add name from spatial data
  gnd = pa_hh$HHS_S02_HROST1$resp_gender,
  rsp_age = pa_hh$HHS_S02_HROST1$resp_age
)

hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("female","male"))) # add names to gender

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- pa_hh$HHS_S03_HROST2 %>%
  dplyr::select(resp_id,age,edu=edu_sch_yrs) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  group_by(resp_id) %>%
  summarise(edu_yrs = ifelse(length(age[edu>=6]>=10)>0,1,0)) %>% # ifelse recode
  dplyr::select(resp_id,edu_yrs) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# edu_chld_att
# No data
hwb_tmp$edu_chld_att <- NA

## HEALTH

# hlt_chld_mt
# No data
hwb_tmp$hlt_chld_mt <- NA

# hlt_fd_sec
# Reported not having enough to eat in the last 12 months
hwb_tmp <- pa_hh$HHS_S09_ASSET %>%
  dplyr::select(resp_id,hlt_fd_sec=food_sec) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(hlt_fd_sec = ifelse(hlt_fd_sec==12,1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_pt
# Did not eat meat in last week, or every week on average over period
hwb_tmp$hlt_pt <- NA

## LIVING STANDARDS

# ls_elec
# A2: Always has enough light in the home
hwb_tmp <- pa_hh$HHS_S09_ASSET %>%
  dplyr::select(resp_id,ls_elec=light_sufficiency) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(ls_elec = ifelse(ls_elec==5,1,0)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_san
# No data
hwb_tmp$ls_san <- NA

# ls_wat
# No data
hwb_tmp$ls_wat <- NA

# ls_hse
# At least one of the three housing materials for roof, walls and floor are inadequate: the floor is of natural materials and/or the roof and/or walls are of natural or rudimentary materials
hwb_tmp <- pa_hh$HHS_S09_ASSET %>%
  dplyr::select(resp_id,main_house_wl,main_house_wl_spfy,main_house_rf,
         main_house_rf_spfy)  %>%
  { . ->> vrs } %>% # keep vars
  mutate(wl=as.numeric(as.factor(ifelse(main_house_wl==4,  # combine other cols, make factor then numeric
                             main_house_wl_spfy,main_house_wl)))) %>%
  mutate(rf=as.numeric(as.factor(ifelse(main_house_rf==4,
                             main_house_rf_spfy,main_house_rf))))  %>% 
  mutate(wl=ifelse(wl %in% c(6,7,8,10,19,20,22),1,0))  %>%  # recode
  mutate(rf=ifelse(rf %in% c(2),1,0)) %>%
  mutate(ls_hse=ifelse(rowSums(dplyr::select(.,wl,rf),na.rm=T)==2,1,0)) %>%
  dplyr::select(resp_id,ls_hse) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# ls_fuel
# No data
hwb_tmp$ls_fuel <- as.numeric(NA)

# ls_ast
# The household does not own more than one of the following items: radio, TV, telephone, bike, motorbike computer, or refrigerator (conditional on not owning a car or truck). Or similar assets in each survey.
hwb_tmp <- pa_hh$HHS_S09_ASSET %>%
  dplyr::select(resp_id,radio_num,bicycle_num,phone_num, # exc. motorbike. computer, fridge. inc. mplayer and dvd
         tv_num,mplayer_num,dvd_num) %>% # exc. other cats as already interated into other cols
  { . ->> vrs } %>% # keep vars
  mutate(ls_ast=ifelse(rowSums(dplyr::select(.,-resp_id),na.rm=T)>1,1,0)) %>%
  dplyr::select(resp_id,ls_ast) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: agricultural land; fishing vessel; livestock
tmp <- pa_hh$HHS_S06_LAND %>% # get land info
  dplyr::select(resp_id,plot_ownership) %>%
  group_by(resp_id) %>%
  summarise(plot_ownership = ifelse(sum(plot_ownership) %in% c(1,3,5,6),1,0)) # recode
hwb_tmp <-  pa_hh$HHS_S09_ASSET %>% # get livestock
  dplyr::select(resp_id, num_cattle:num_other_liv) %>%
  mutate_at(vars(num_cattle:num_other_liv),list(~.-1)) %>% # make zero based
  full_join(tmp) %>%
  { . ->> vrs } %>% # keep vars
  mutate(lv_pas = ifelse(rowSums(dplyr::select(.,-resp_id),na.rm=T)>0,1,0)) %>% # recode again
  dplyr::select(resp_id,lv_pas) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

pa_pa <- pa_hh$HHS_S06_LAND %>% # get land info
  dplyr::select(resp_id,site,plot_area,plot_seed_qty)
pa_pa <- merge(pa_pa,pa_hh$HHS_S01_INFO[c("resp_id", "fokontany")],
               by = "resp_id", all.x=T)
write.csv(pa_pa,"pa_pa.csv")

## RISK
# rk_exp
# Experienced two shocks in the last year
hwb_tmp$rk_exp <-  as.numeric(NA) # no data

## SUBJECTIVE WELLBEING
# no data
hwb_tmp$swb <- as.numeric(NA)

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
hwb_tmp <- pa_hh$HHS_S10_SOCAP %>%
  dplyr::select(resp_id,ends_with("_provider"),starts_with("mem_type")) %>%
  na_if("") %>%
  { . ->> vrs } %>% # keep vars
  mutate(rwb_cm_st = ifelse(rowSums(!is.na(dplyr::select(.,-resp_id)), # ifelse record
                                    na.rm=T)>0,1,0)) %>%
  dplyr::select(resp_id,rwb_cm_st) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# Community agency
# rwb_cm_ag
# No data
hwb_tmp <- pa_hh$HHS_S10_SOCAP %>%
  dplyr::select(resp_id,rwb_cm_ag =community_help) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(rwb_cm_ag = ifelse(rwb_cm_ag>0,1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# Alternative 2: No assistance from extended family if serious problem
hwb_tmp <- pa_hh$HHS_S10_SOCAP %>%
  dplyr::select(resp_id,rwb_fm_ag =ext_fam_help) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(rwb_fm_ag = ifelse(rwb_fm_ag>0,1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## c) Check variables and tidy  ###################################

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# update id name
names(hwb_tmp)[names(hwb_tmp)=="resp_id"] <- "pj_hhid"

# check col classes before merge
sapply(hwb_tmp,class)

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)] 

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(pa_hh,hwb_tmp)

```

**7. PIMA **
```{r pima, message = FALSE, warning = FALSE}

#### a) get data #####################
# PIMA did a full survey with the male householdhead and a different, partial survey
# in a subset of households with the wife. Most responses on material WB indicators 
# are in the full survey, so I mainly use those here, supplemented by responses
# from the wife survey where indicated.
# Some of the responses from the wife survey could also be included in the monetary liveilhoods
# indicators and/or moderating factors datasets.


## i) household head survey
pi_hh <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,
                         "../data/raw/sango/PIMA/2-PIMA_HHHEAD/PIMA_HHHEAD_SURVEY.CSV")

# deal with null values
pi_hh[pi_hh=="null"] <- NA
pi_hh[pi_hh==-7] <- NA
pi_hh[pi_hh==-8] <- NA
pi_hh[pi_hh==-9] <- NA
pi_hh[pi_hh==""] <- NA

# the following households has data entry errors so removing
# household 692, village 7. Q10 
pi_hh <- subset(pi_hh, !(pi_hh$q1.1 == 7) | !(pi_hh$q1.2 == 692))
# household 369. vullage 30. q4.2.5
pi_hh <- subset(pi_hh, !(pi_hh$q1.1 == 30) | !(pi_hh$q1.2 == 369))

# make unique household ID
pi_hh$IDNO <- paste0(pi_hh$q1.1,"_",pi_hh$q1.2,sep="")

## ii) wife survey

# household wife survey
pi_wf <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,
                         "../data/raw/sango/PIMA/3-PIMA_WIFE/PIMA_WIFE_SURVEY.CSV")
# deal with null values
pi_wf[pi_wf=="null"] <- NA
pi_wf[pi_wf==-7] <- NA
pi_wf[pi_wf==-17] <- NA
pi_wf[pi_wf==-8] <- NA
pi_wf[pi_wf==-9] <- NA
pi_wf[pi_wf==""] <- NA
# make null NA
pi_wf[pi_wf=="null"] <- NA

# make unique ID
pi_wf$IDNO <- paste0(pi_wf$q1.1,"_",pi_wf$q1.2,sep="")

# checking contribution of ES to env income.
# tmp <- pi_hh %>%
#   select(q1.1,q9.1.1:q9.1.9,q10.1.1:q10.1.6) %>%
#   mutate_at(vars(q9.1.1:q9.1.9),as.numeric) %>% # get pc of types of env income
#   mutate_at(vars(q9.1.1:q9.1.9),funs(./50)) %>%
#   mutate_at(vars(q10.1.1:q10.1.6),as.numeric) %>% # get pc of types of livelihoods
#   mutate_at(vars(q10.1.1:q10.1.6),funs(./25)) %>%
#   mutate(fish_pc_tot_lvl=q9.1.5 * q10.1.3) %>% # get fish as % of total livelihood
#   filter(fish_pc_tot_lvl>0) %>% # 75 out of 1922 hh report income from fisheries. 1%
#   filter(fish_pc_tot_lvl>0.05) # 17 report an income of between 5% and 10%
#   # 4 report an income of over 10%
#   summarise(fish_pc_env_inc=max(q9.1.5))



## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS
hwb_tmp <- data.frame(stringsAsFactors = F,
  IDNO = pi_hh$IDNO,
  pjnm = "pi",
  cn = "TZA",
  yr = 2015,
  admn1 = as.character(NA), # to add name from spatial data
  admn2 = as.character(NA), # to add name from spatial data
  admn3 = as.character(NA), # to add name from spatial data
  admn4 = as.character(NA), # need village names linked to IDs from PIMA ppl
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = as.character(pi_hh$q1.1), 
  ses = as.character(NA), 
  gnd = pi_hh$q2.0,
  rsp_age = as.numeric(pi_hh$q2.1)
)

hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("male","female"))) # add names to gender

## EDUCATION 

# edu_yrs
# Alternative 1: Household head has not completed more than six years of schooling
hwb_tmp <- pi_hh %>%
  dplyr::select(IDNO,edu_yrs=q2.2) %>%
  { . ->> vrs } %>% # keep vars
  mutate(edu_yrs = ifelse(edu_yrs<=6,0,1)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# edu_chld_att
# No data
hwb_tmp$edu_chld_att <- NA

## HEALTH

# hlt_chld_mt
# Severe illness of breadwinner in last year
hwb_tmp <- pi_hh %>%
  dplyr::select(IDNO,hlt_chld_mt=q4.2.2) %>%
  mutate(hlt_chld_mt=ifelse(hlt_chld_mt>0,1,0))%>%
  full_join(hwb_tmp,.)

# hlt_fd_sec
# No data
hwb_tmp <- pi_wf %>%
  dplyr::select(IDNO,hlt_fd_sec=q7.1) %>%
  { . ->> vrs } %>% # keep vars
  mutate(hlt_fd_sec = ifelse(hlt_fd_sec>2,1,0))%>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_pt
# Did not eat meat in last week, or every week on average over period
hwb_tmp <- pi_hh %>%
  dplyr::select(IDNO,hlt_pt=q7.1.1) %>%
  { . ->> vrs } %>% # keep vars
  mutate(hlt_pt = ifelse(hlt_pt %in% c(1,2),1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVING STANDARDS

# ls_elec
# No data
hwb_tmp$ls_elec <- as.numeric(NA)

# ls_san
# No data
hwb_tmp$ls_san <- as.numeric(NA)

# ls_wat
# No data
hwb_tmp$ls_wat <- as.numeric(NA)

# ls_hse
# No data
hwb_tmp$ls_hse <- as.numeric(NA)
  
# ls_fuel
# No data
hwb_tmp$ls_fuel <- as.numeric(NA)

# ls_ast
# No data
hwb_tmp$ls_ast <- as.numeric(NA)

## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: agricultural land; fishing vessel; livestock
hwb_tmp <- pi_hh %>%
  dplyr::select(IDNO,q5.1.3,q6.0) %>%
  { . ->> vrs } %>% # keep vars
  mutate(lv_pas = ifelse(rowSums(dplyr::select(.,-IDNO),na.rm=T)>0,1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# pi_pa <- pi_hh %>%
#   dplyr::select(IDNO,WMA.nonWMA,q1.1,q6.1.2.1,q6.1.2.2,q6.1.2.3)
# names(pi_pa) <- c("hhid","WMA","vlid","cows","bulls","calves")
# write.csv(pi_pa,"pi_pa.csv")

## RISK
# rk_exp
# Experienced two shocks in the last year
hwb_tmp <- pi_hh %>%
  dplyr::select(IDNO,rk_exp=q4.1) %>%
  { . ->> vrs } %>% # keep vars
  mutate(rk_exp = ifelse(rk_exp==1,0,1)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## SUBJECTIVE WELLBEING
# no data
hwb_tmp$swb <- as.numeric(NA)

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
hwb_tmp <- pi_hh %>%
  dplyr::select(IDNO,rwb_cm_st=q5.5) %>%
  { . ->> vrs } %>% # keep vars
  mutate(rwb_cm_st = ifelse(rwb_cm_st %in% c(0,1),0,1)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# Community agency
# rwb_cm_ag
# Alternative 2: Feels unable to exert influence on decisions in NRM organisation asked about in the survey

hwb_tmp <- pi_hh %>%
  dplyr::select(IDNO,rwb_cm_ag=q11.9,q1.2) %>%
  group_by(q1.2) %>%
  mutate(rwb_cm_ag=replace(rwb_cm_ag, which(is.na(rwb_cm_ag)), 
                           getmode(rwb_cm_ag[!is.na(rwb_cm_ag)]))) %>%
  ungroup() %>%
  { . ->> vrs } %>% # keep vars
  mutate(rwb_cm_ag=ifelse(rwb_cm_ag==1,1,0)) %>%
  mutate(rwb_cm_ag = replace(rwb_cm_ag, which(is.na(rwb_cm_ag)),0)) %>%
  select(-q1.2) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# No data
hwb_tmp$rwb_fm_ag <- as.numeric(NA) # no data

## c) Check variables and tidy  ###################################

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# update id name
names(hwb_tmp)[names(hwb_tmp)=="IDNO"] <- "pj_hhid"

# check col classes before merge
sapply(hwb_tmp,class)

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)] 

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(pi_hh,pi_wf,hwb_tmp)

```

**8. ACES **
```{r aces, message = FALSE, warning = FALSE}

#### a) get all data csvs in list object  #####################
nm <- list.files("../data/raw/sango/ACES/HHSURVEY/data",full.names=T)
ac_hh <- list()
for (i in 1:length(nm)){
  ac_hh[[i]] <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nm[i])
  names(ac_hh)[i] <- strsplit(nm[i],"/")[[1]][8]
  names(ac_hh)[i] <- strsplit( names(ac_hh)[i],"_anon")[[1]][1]
  names(ac_hh)[i] <- strsplit( names(ac_hh)[i],"_che")[[1]][1]
  ac_hh[[i]][ac_hh[[i]]==""] <- NA # convert NAs
  ac_hh[[i]][ac_hh[[i]]=="skipped"] <- NA
  ac_hh[[i]][ac_hh[[i]]=="nao_sabe"] <- NA
  ac_hh[[i]][ac_hh[[i]]=="unknown"] <- NA
  ac_hh[[i]][ac_hh[[i]]=="Mucavango_2_not_on_frame"] <- # correct a village name
    "Mucavango_2"
}

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS
hwb_tmp <- data.frame(stringsAsFactors = F,
  hh_survey_id = ac_hh$a_household$hh_survey_id,
  pjnm = "ac",
  cn = as.character("MOZ"),
  yr = 2015,
  admn1 = ac_hh$a_household$province, # to add name from spatial data
  admn2 = ac_hh$a_household$district, # to add name from spatial data
  admn3 = ac_hh$a_household$admin_post,
  admn4 = ac_hh$a_household$village,
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = NA, 
  ses = as.character(NA) # to add name from spatial data
)

hwb_tmp <- ac_hh$b_household %>%
  dplyr::select(hh_survey_id,gnd=sex,rsp_age=age_years) %>%
  group_by(hh_survey_id) %>%
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)

hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("female","male"))) # add names to gender

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- ac_hh$b_household %>%
  dplyr::select(hh_survey_id,edu=highest_education_level,age=age_years) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(edu = as.numeric(as.factor(edu))) %>%  # convert edu to numeric codes
  group_by(hh_survey_id) %>% 
  summarise(edu_yrs = ifelse(length(age[edu %in% c(6,14:23)]>=10)>0,1,0)) %>% # ifelse recode
  dplyr::select(hh_survey_id,edu_yrs) %>%
  full_join(hwb_tmp,.) %>%
  mutate(edu_yrs = replace(edu_yrs, is.na(edu_yrs),0)) # assuming NA is zero
# codes
lvls(vrs)

# edu_chld_att
# Any school-aged child is not attending school for at least six years
hwb_tmp <- ac_hh$b_household %>%
  dplyr::select(hh_survey_id,edu=recent_school_attendance,age=age_years) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(edu = as.numeric(as.factor(edu))) %>%  # convert edu to numeric codes
  group_by(hh_survey_id) %>%
  summarise(edu_chld_att = ifelse(length(age[edu %in% c(2)]<=12)>0,1,0))  %>% # ifelse recode
  dplyr::select(hh_survey_id,edu_chld_att) %>%
  full_join(hwb_tmp,.) %>%
  mutate(edu_chld_att = replace(edu_chld_att, is.na(edu_chld_att),0)) # assuming NA is zero
# codes
lvls(vrs)

## HEALTH

# hlt_chld_mt
#  Alternative 1: has any child below 5 years died in the last year
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id,hlt_chld_mt = infant_death) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(hlt_chld_mt = as.numeric(factor(hlt_chld_mt))) %>% # get var as numeric
  mutate(hlt_chld_mt = hlt_chld_mt - 1) %>% # make zero based
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_fd_sec
# Reported not having enough to eat in the last 12 months
hwb_tmp <- ac_hh$h_food_shortage %>%
  dplyr::select(hh_survey_id=hh_id, hlt_fd_sec = type) %>%
  # group_by(hlt_fd_sec) %>%
  # tally()
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(hlt_fd_sec = as.numeric(as.factor(hlt_fd_sec))) %>% # get as numeric
  group_by(hh_survey_id) %>%
  summarise(hlt_fd_sec = ifelse(length( # recode
  hlt_fd_sec[hlt_fd_sec%in%c(68)])>0,1,0)) %>%
  full_join(hwb_tmp,.) %>%
  mutate(hlt_fd_sec = replace(hlt_fd_sec, is.na(hlt_fd_sec),1)) # assuming NA is zero
# codes
lvls(vrs)

# hlt_pt
# Did not eat meat in last week, or every week on average over period

hwb_tmp <- ac_hh$h_source_protein %>%
  dplyr::select(hh_survey_id=hh_id, hlt_pt = frequency_unit) %>%
  { . ->> vrs } %>% # keep vars
  mutate(hlt_pt = as.numeric(as.factor(hlt_pt))) %>% # get as numeric
  group_by(hh_survey_id) %>%
  summarise(hlt_pt = ifelse(length( # recode
  hlt_pt[!(hlt_pt%in%c(4,8,26,28,30,35:43))])>0,1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

#hwb_tmp$hlt_pt[is.na(hwb_tmp$hlt_pt)] <- 0 # assuming NAs are zero

## LIVING STANDARDS

# ls_elec
# no data
hwb_tmp$ls_elec <- NA

# ls_san
# The household’s sanitation facility is not flush toilet or latrine, or ventilated improved pit or composting toilet
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id,ls_san = bathroom_type) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_san = ifelse(as.numeric(as.factor(ls_san)) %in% c(6,7,8),1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_wat
# Is not piped water, public tap, borehole or pump, protected well, protected spring or rainwater
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id,wat1=water_source_wet_season,wat2=water_source_dry_season) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(wat1 = ifelse(as.numeric( # convert vars to numeric then recode
    as.factor(wat1)) %in% c(2,12,13),0,1)) %>%
    mutate(wat2 = ifelse(as.numeric(
    as.factor(wat2)) %in% c(2,6,7,9,11,17),0,1)) %>%
  mutate(ls_wat = ifelse(rowSums(dplyr::select(.,wat1,wat2),na.rm=T)==2,1,0)) %>% # recode
  dplyr::select(hh_survey_id,ls_wat) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_hse
# At least one of the three housing materials for roof, walls and floor are inadequate: the floor is of natural materials and/or the roof and/or walls are of natural or rudimentary materials
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id,wl=wall_material,rf=roof_material,fl=floor_material) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(wl = ifelse(as.numeric(as.factor(wl)) %in% # recode as numeric
                       c(1,4,8,9,12,13,15:18,24,27,28),0,1)) %>%
  mutate(rf = ifelse(as.numeric(as.factor(rf)) %in% # recode as numeric
                       c(1,2,6,7,8,9,10),0,1)) %>%
  mutate(fl = ifelse(as.numeric(as.factor(fl)) %in% # recode as numeric
                       c(1,2,6),0,1)) %>%
  mutate(ls_hse = ifelse(rowSums(dplyr::select(.,wl,rf,fl),na.rm=T)>=2,1,0)) %>% # make variable
  dplyr::select(hh_survey_id,ls_hse) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# ls_fuel
# The household cooks with dung or wood
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id,ls_fuel = principal_fuel) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_fuel = ifelse(as.numeric(factor(ls_fuel)) %in% c(1:4),0,1))%>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  

# ls_ast
# The household does not own more than one of the following items: radio, TV, telephone, bike, motorbike computer, or refrigerator (conditional on not owning a car or truck). Or similar assets in each survey.
hwb_tmp <- ac_hh$i_asset %>%
  dplyr::select(hh_survey_id=hh_id,ls_ast=asset_type) %>% # no computer
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_ast = as.numeric(factor(ls_ast))) %>% # make numeric codes
  group_by(hh_survey_id) %>%
  summarise(ls_ast = ifelse(length(ls_ast[ # recode
    ls_ast %in% c(30,50,55,95,108,122,140,153)])>1,1,0))%>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: > 1ha agricultural land; fishing vessel; livestock
tmp <- ac_hh$g_land_extra.csv %>% # get land
  dplyr::select(hh_survey_id=hh_id,area_owned) %>%
  mutate(area_owned = ifelse(area_owned>=1,1,0)) # recode
hwb_tmp <- ac_hh$h_livestock %>% # get livestock
  dplyr::select(hh_survey_id=hh_id,quantity) %>%
  right_join(tmp) %>%
  { . ->> vrs } %>% # keep vars
  mutate(lv_pas = ifelse(rowSums(dplyr::select(.,-hh_survey_id),na.rm=T)>0,1,0)) %>% # recode again
  group_by(hh_survey_id) %>%
  summarise(lv_pas= ifelse(sum(lv_pas,na.rm=T)>0,1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ac_pa <- ac_hh$g_land_extra.csv %>% # get land
#   dplyr::select(hh_survey_id=hh_id,area_owned)
# ac_pa <- merge(ac_pa,ac_hh$a_household[c("hh_survey_id", "village","district")],
#                by="hh_survey_id", all.x = T)
# write.csv(ac_pa,"ac_pa.csv")

## RISK
# rk_exp
# Experienced two shocks in the last year
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id,rk_exp=household_shortfall) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rk_exp = ifelse(as.numeric(factor(rk_exp))==1,0,1))%>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## SUBJECTIVE WELLBEING
# swb
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id, swb=subj_wellbeing_life_general) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(swb= as.character(swb)) %>% # make character
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id,st1=receive_advice,st2=farmers_assoc_member) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(st1 = ifelse(as.numeric(factor(st1))==2,0,1)) %>% # recode underlying vars
  mutate(st2 = ifelse(as.numeric(factor(st2))==1,0,1)) %>%
  mutate(rwb_cm_st = ifelse(rowSums(dplyr::select(.,st1,st2),na.rm=T)>0,1,0)) %>%
  dplyr::select(hh_survey_id,rwb_cm_st) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Community agency
# rwb_cm_ag
# Disatissfied (or below) with friendships or community support
hwb_tmp <- ac_hh$a_household %>%
  dplyr::select(hh_survey_id,rwb_cm_ag=subj_wellbeing_treatment_of_family) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_cm_ag = ifelse(as.numeric(factor(rwb_cm_ag)) %in% c(1,2,4),0,1))  %>%
  dplyr::select(hh_survey_id,rwb_cm_ag) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# No data
hwb_tmp$rwb_fm_ag <- as.numeric(NA) # no data

## c) Check variables and tidy  ###################################

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# update id name
names(hwb_tmp)[names(hwb_tmp)=="hh_survey_id"] <- "pj_hhid"
hwb_tmp$pj_hhid <- as.character(hwb_tmp$pj_hhid)

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)] 

# check col classes before merge
sapply(hwb_tmp,class)

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(ac_hh,hwb_tmp)

```

**9. SENTINEL **
```{r sentinel, message = FALSE, warning = FALSE}

#### a) get data in list of csvs #####################

sen <- list()
nm <- c("sett","assoc","for","prod","hh","af")
for(i in 1:6){
  sen[[i]] <- openxlsx::read.xlsx("../data/raw/sentinel/ATREE-WGSL_Data.xlsx",
                 sheet = i, colNames=TRUE)
  names(sen)[i] <- nm[i]
  sen[[i]] <- as.data.frame(sapply(sen[[i]],function(x) gsub("  .*","",x))) # convert weird spaces to NAs
  sen[[i]][sen[[i]]==""] <- NA
  sen[[i]][sen[[i]]==" "] <- NA
  sen[[i]][sen[[i]]==-96] <- NA
  
  sen[[i]][sen[[i]]=="CHAMARAJANAGARA"] <- "CHAMARAJANAGAR" # fix some names
  sen[[i]][sen[[i]]=="Chamarajanagar"] <- "CHAMARAJANAGAR"
  sen[[i]][sen[[i]]=="Kodagu"] <- "KODAGU"
  
}

sen$hh$IDNO <- paste(sen$hh$HHID,"_",sen$hh$SID,sep="") # make unique hh id vil + site

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS
hwb_tmp <- data.frame(
  IDNO = as.character(sen$hh$IDNO), # unique id vil + site
  pjnm = "se",
  cn = "IND",
  yr = 2014,
  admn1 = NA, # to add name from spatial data
  admn2 = as.character(sen$hh$HDNAME), # to add name from spatial data
  admn3 = NA, # to add name from spatial data
  admn4 = NA, # to add name from spatial data
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = as.character(sen$hh$SID), 
  ses = NA, # to add from other data
  gnd = sen$hh$RESGEN,
  rsp_age = as.numeric(as.character(sen$hh$HHMAGE_01))
)

hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("male", "female"))) # add names to gender

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,starts_with("HHMAGE_"),starts_with("HHMHGRADE_")) %>%
  gather(v, value, HHMAGE_01:HHMHGRADE_12) %>% # reshape
  separate(v, c("var", "col")) %>%
  arrange(IDNO) %>%
  spread(var, value) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(edu = as.numeric(factor(HHMHGRADE))) %>% # make schooling a factor
  mutate_at(c("HHMAGE"), as.numeric) %>%
  group_by(IDNO) %>% 
  summarise(edu_yrs = ifelse(length(
    HHMAGE[edu %in% c(1:5,22:23,27:31,33:64)]>=10)>0,0,1)) %>%
  dplyr::select(IDNO,edu_yrs) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# edu_chld_att
# Any school-aged child is not attending school for at least six years
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,starts_with("HHMAGE_"),starts_with("HHMSCHCATT_")) %>%
  gather(v, value, HHMAGE_01:HHMSCHCATT_12) %>% # reshape
  separate(v, c("var", "col")) %>%
  arrange(IDNO) %>%
  spread(var, value) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(c("HHMAGE","HHMSCHCATT"), as.numeric) %>%
  group_by(IDNO) %>%
  summarise(edu_chld_att = ifelse(
    length(HHMSCHCATT[HHMAGE >= 6 & HHMAGE <=10] %in% c(2))>0,0,1))  %>% # ifelse recode
  dplyr::select(IDNO,edu_chld_att) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## HEALTH

# hlt_chld_mt
# Severe illness in family in last year
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,starts_with("SHCK11")) %>%
  mutate(hlt_chld_mt=ifelse(SHCK11==1,0,1)) %>%
  dplyr::select(IDNO,hlt_chld_mt) %>%
  full_join(hwb_tmp,.)

# hlt_fd_sec
# Reported not having enough to eat in the last 12 months
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,	FSHRTGYR) %>%
  { . ->> vrs } %>% # keep vars
  #mutate_at(vars(starts_with("FSHRTGYR")), as.numeric) %>%
  mutate(hlt_fd_sec = ifelse(FSHRTGYR==1,0,1)) %>%
  dplyr::select(IDNO,hlt_fd_sec) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_pt
# Did not eat meat in last week, or every week on average over period
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,hlt_pt=FOODTYP5FTYPE_CONS) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(hlt_pt = ifelse(hlt_pt==0,0,1)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVING STANDARDS

# ls_elec
# A1: Main source of light is not electric mains
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO, ls_elec = HHLSRCE) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_elec = ifelse(ls_elec==1,1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_san
# The household’s sanitation facility is not flush toilet or latrine, or ventilated improved pit or composting toilet
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO, ls_san = TLTFCTY) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_san = as.numeric(as.factor(ls_san))) %>% # make numeric codes
  mutate(ls_san = ifelse(ls_san %in% c(1,7:9),1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_wat
# Is not piped water, public tap, borehole or pump, protected well, protected spring or rainwater
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO, ls_wat = H20SCE) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_wat = as.numeric(as.factor(ls_wat))) %>% # make numeric codes
  mutate(ls_wat = ifelse(ls_wat %in% c(1:2,4),1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_hse
# At least one of the three housing materials for roof, walls and floor are inadequate: the floor is of natural materials and/or the roof and/or walls are of natural or rudimentary materials
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO, wl=WALLMTL, fl = FLRMTL) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(wl = ifelse(wl %in% c(11,12,14,15),0,1)) %>% # recode underlying vars
  mutate(fl = ifelse(fl %in% c(4:6),0,1)) %>%  
  mutate(ls_hse = ifelse(rowSums(dplyr::select(.,wl,fl),na.rm=T)==2,1,0)) %>%
  dplyr::select(IDNO,ls_hse) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# ls_fuel
# The household cooks with dung or wood
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO, ls_fuel =HHCKNFUEL) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_fuel = ifelse(ls_fuel %in% c(1,6:8),0,1)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# ls_ast
# The household does not own more than one of the following items: radio, TV, telephone, bike, motorbike computer, or refrigerator (conditional on not owning a car or truck). Or similar assets in each survey.
hwb_tmp <- sen$hh %>% # no telephone
  dplyr::select(IDNO,ANOOWND_05,ANOOWND_06,ANOOWND_18,ANOOWND_17,ANOOWND_04) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(starts_with("ANO")), # recode all underlying vars
            .funs=list(~ ifelse(.==0,0,1))) %>%
  mutate(ls_ast = ifelse(rowSums(dplyr::select(.,starts_with("ANO")),na.rm=T)>1,
                         1,0)) %>% # recode
  dplyr::select(IDNO,ls_ast) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: > 1ha agricultural land; fishing vessel; livestock
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,starts_with("PTENURE_"),starts_with("ESTNO_"))%>% 
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(starts_with("PTENURE_")), # make underlying vars numeric codes then recode
            .funs=list(~ ifelse(as.numeric(factor(.)) %in% c(1,2),1,0))) %>%
  mutate_at(.vars=vars(starts_with("ESTNO_")), # make underlying vars numeric codes then recode
            .funs=list(~ ifelse(as.numeric(factor(.))>1,1,0))) %>%
  mutate(lv_pas = ifelse(rowSums(dplyr::select(.,-IDNO),na.rm=T)>0,1,0)) %>%
  dplyr::select(IDNO,lv_pas) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## RISK
# rk_exp
# Experienced two shocks in the last year
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,SHCK1:SHCKOTR) %>%
  { . ->> vrs } %>% # keep vars
  mutate(SHCKOTR = ifelse(!is.na(SHCKOTR),2,1)) %>% # align other field code
  mutate_at(.vars=vars(starts_with("SHC")), # recode all underlying vars
            .funs=list(~ ifelse(.==1,0,1))) %>%
  mutate(rk_exp = ifelse(rowSums(dplyr::select(.,starts_with("SHC")),na.rm=T)<13,
                         1,0)) %>%  # recode
  dplyr::select(IDNO, rk_exp) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## SUBJECTIVE WELLBEING
# swb
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO, swb = WLIFE) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(swb = as.character(factor(swb,labels=c(# add labels and make character
    "Very satisfied",
    "Satisfied",
    "Neither satisfied nor dissatisfied",
    "Dissatisfied",
    "Very dissatisfied")))) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,RTVGOV,CRTV_VPOS) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate_at(.vars=vars(RTVGOV,CRTV_VPOS), # recode all underlying vars
            .funs=list(~ ifelse(.==1,1,0))) %>%
  mutate(rwb_cm_st = ifelse(rowSums(dplyr::select(.,RTVGOV,CRTV_VPOS),na.rm=T)>0,
                         1,0)) %>%  # recode
  dplyr::select(IDNO,rwb_cm_st) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Community agency
# rwb_cm_ag
# Disatissfied (or below) with friendships or community support
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO,rwb_cm_ag=WCSPRT) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_cm_ag = ifelse(rwb_cm_ag %in% c(4,5),0,1)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family opportunity structures
# rwb_fm_st
# No close relatives in the village
hwb_tmp <- sen$hh %>%
  dplyr::select(IDNO, rwb_fm_st = HHRTVS) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_fm_st = ifelse(rwb_fm_st==1,1,0)) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family agency
# rwb_fm_ag
# No data
hwb_tmp$rwb_fm_ag <- as.numeric(NA) # no data

## c) Check variables and tidy  ###################################

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# update id name
names(hwb_tmp)[names(hwb_tmp)=="IDNO"] <- "pj_hhid"
hwb_tmp$pj_hhid <- as.character(hwb_tmp$pj_hhid)

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)] 

# check col classes before merge
sapply(hwb_tmp,class)

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(sen,hwb_tmp)

```

**10. ASSETS - COLOMBIA **
```{r assets, message = FALSE, warning = FALSE}

#### a) get all data csvs in list object  #####################
# ASSETS did surveys in two rounds. To save on code, for each survey section, I combine the csv into one dataframe with a unique response id (wave + hh id). Values for 
# each wave can be seperated or aggregated later as needed

nm1 <- list.files("../data/raw/assets_colombia_initial_unpublished/Colombia/W1CSV",pattern="*.csv",full.names=T)
nm2 <- list.files("../data/raw/assets_colombia_initial_unpublished/Colombia/W2CSV",pattern="*.csv",full.names=T)
asc_hh <- list()
for (i in 1:length(nm1)){
  wv1 <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nm1[i])
  wv1$wv <- 1 # wave number
  wv1$IDNO <- paste(wv1$wv,wv1$Resguardo, wv1$Comunidad, 
                    wv1$Hogar,sep="_") # unique response ID
  wv2 <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nm2[i])
  names(wv2) <- gsub( "W2", "", names(wv2)) # fix wv2 names
  wv2$wv <- 2 # wave number
  wv2$IDNO <- paste(wv2$wv,wv2$Resguardo, wv2$Comunidad, 
                    wv2$Hogar,sep="_") # unique response ID
  asc_hh[[i]] <- plyr::rbind.fill(wv1,wv2)
  names(asc_hh)[i] <- strsplit(nm1[i],"/")[[1]][7]
  names(asc_hh)[i] <- paste0(strsplit(names(asc_hh)[i],"_")[[1]][c(3,5)],collapse="_")
  names(asc_hh)[i] <- stringr::str_sub(names(asc_hh)[i],1,-5)
  
  # convert NAs
  asc_hh[[i]][asc_hh[[i]]==""] <- NA
  asc_hh[[i]][asc_hh[[i]]=="-999"] <- NA
  asc_hh[[i]][asc_hh[[i]]=="-998"] <- NA
  asc_hh[[i]][asc_hh[[i]]=="-997"] <- NA
  asc_hh[[i]][asc_hh[[i]]=="-888"] <- NA
  asc_hh[[i]]$hhid <- paste(asc_hh[[i]]$Resguardo, # add hhid
                            asc_hh[[i]]$Comunidad,
                            asc_hh[[i]]$Hogar, sep="_")
}

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS
hwb_tmp <- data.frame(stringsAsFactors = F,
  IDNO = asc_hh$A_InterviewDetails$IDNO, # wave number + hogar
  hhid = asc_hh$A_InterviewDetails$Hogar, # for aggregating later. then remove
  pjnm = "asc",
  cn = as.character("COL"),
  yr = 2014,
  admn1 = as.character(NA), # to add name from spatial data
  admn2 = as.character(NA), # to add name from spatial data
  admn3 = asc_hh$A_InterviewDetails$Resguardo,
  admn4 = asc_hh$A_InterviewDetails$Comunidad,
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = NA, 
  ses = as.character(NA) # to add name from spatial data
)

hwb_tmp <- asc_hh$B_Roster %>%
  dplyr::select(IDNO,gnd=b_2,rsp_age=b_5_b) %>%
  group_by(IDNO) %>%
  filter(row_number()==1) %>%
  mutate(rsp_age= 2014-rsp_age) %>%
  full_join(hwb_tmp,.)

hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("male","female"))) # add names to gender

hwb_tmp[hwb_tmp=="Madroño"] <- "Madrono" # align some village names
hwb_tmp[hwb_tmp=="Bakuri"] <- "Bacuri"
hwb_tmp[hwb_tmp=="Puerto Cordoba"] <- "Pto Cordoba"

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- bind_cols(asc_hh$B_Roster[c("IDNO","b_5_b")],asc_hh$C_Education[c("c_6")]) %>%
  { . ->> vrs } %>%  # keep vars
  mutate(age=2014-b_5_b,edu=as.numeric(factor(c_6))) %>% 
  group_by(IDNO) %>% 
  summarise(edu_yrs = ifelse(length(age[edu %in% c(1:2,9:14)]>=10)>0,1,0)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# edu_chld_att
# Any school-aged child is not attending school for at least six years
hwb_tmp <- bind_cols(asc_hh$B_Roster[c("IDNO","b_5_b")],asc_hh$C_Education[c("c_8")]) %>%
  { . ->> vrs } %>%  # keep vars
  mutate(age=2014-b_5_b,edu=as.numeric(factor(c_8))) %>% 
  group_by(IDNO)  %>% 
  summarise(edu_chld_att = ifelse(length(age[edu %in% c(1)]<=12)>0,1,0))  %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## HEALTH

# hlt_chld_mt
#  Alternative 1: has any child below 5 years died in the last year
hwb_tmp <- asc_hh$E_Maternity %>%
  dplyr::select(IDNO,hlt_chld_mt=e_8) %>%
  { . ->> vrs } %>% # keep vars
  mutate(hlt_chld_mt= as.numeric(factor(hlt_chld_mt))) %>%
  group_by(IDNO) %>%
  summarise(hlt_chld_mt=ifelse(c(2) %in% hlt_chld_mt,0,1)) %>% # assuming NA is No
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_fd_sec
# Reported not having enough to eat in the last 12 months
hwb_tmp <- asc_hh$J_FoodSecurity %>%
  dplyr::select(IDNO,j_1_c:j_1_d) %>%
  { . ->> vrs } %>% # keep vars
    mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(hlt_fd_sec=ifelse(rowSums(dplyr::select(.,-IDNO),na.rm=T)>0,0,1)) %>%
  dplyr::select(IDNO,hlt_fd_sec) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_pt
# Did not eat meat in last week, or every week on average over period
hwb_tmp <- asc_hh$I_FoodRoster %>%
  dplyr::select(IDNO,FoodID,i_2) %>%
  filter(FoodID %in% # keep rows applying to meat
           unique(FoodID)[c(1:59,185:186,189:191,199:201)]) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(FoodID,i_2) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(hlt_pt=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(hlt_pt=sum(hlt_pt,na.rm=T)) %>% # summarise for HH
  mutate(hlt_pt=ifelse(hlt_pt>0,1,0)) %>% # recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVING STANDARDS

# ls_elec
# no data
hwb_tmp <- asc_hh$H_Housing %>%
  dplyr::select(IDNO,ls_elec=h_20) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_elec = ifelse(ls_elec=="No",0,1)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_san
# The household’s sanitation facility is not flush toilet or latrine, or ventilated improved pit or composting toilet
hwb_tmp <- asc_hh$H_Housing %>%
  dplyr::select(IDNO, ls_san=h_32) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_san = as.numeric(factor(ls_san))) %>% # make numeric code
  mutate(ls_san = ifelse(ls_san %in% c(1,3),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_wat
# Is not piped water, public tap, borehole or pump, protected well, protected spring or rainwater
hwb_tmp <- asc_hh$H_Housing %>%
  dplyr::select(IDNO, ls_wat=h_25) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_wat = as.numeric(factor(ls_wat))) %>%  # make numeric code
  mutate(ls_wat = ifelse(ls_wat %in% c(1,2),1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_hse
# At least one of the three housing materials for roof, walls and floor are inadequate: the floor is of natural materials and/or the roof and/or walls are of natural or rudimentary materials
hwb_tmp <- asc_hh$H_Housing %>%
  dplyr::select(IDNO, wl=h_5, rf= h_6, fl= h_7)  %>%
  { . ->> vrs }  %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))))   %>% 
  mutate(wl = ifelse(wl %in% c(3,6),1,0))  %>% # recode underlying vats
  mutate(rf = ifelse(rf %in% c(1),1,0)) %>%
  mutate(fl= ifelse(fl %in% c(1,7,8),1,0)) %>%
  mutate(ls_hse = ifelse(rowSums(dplyr::select(.,-IDNO))<2,0,1)) %>% # make var
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  dplyr::select(IDNO,ls_hse) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# ls_fuel
# The household cooks with dung or wood
hwb_tmp <- asc_hh$H_Housing %>%
  dplyr::select(IDNO,ls_fuel=h_9) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_fuel=as.numeric(factor(ls_fuel))) %>% # make numeric code
  mutate(ls_fuel=ifelse(ls_fuel==1,0,1)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_ast
# The household does not own more than one of the following items: radio, TV, telephone, bike, motorbike computer, or refrigerator (conditional on not owning a car or truck). Or similar assets in each survey.
hwb_tmp <- asc_hh$L_DurableGoods %>%
  dplyr::select(IDNO,DurableGoodID,l_1) %>%
  filter(DurableGoodID %in% # keep rows applying relevant goods
           unique(DurableGoodID)[c(1,2,19,24,10)]) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(DurableGoodID,l_1) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(ls_ast=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(ls_ast=sum(ls_ast,na.rm=T)) %>% # summarise for HH
  mutate(ls_ast=ifelse(ls_ast>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: > 1ha agricultural land; fishing vessel; livestock

res <- hwb_tmp[1]
tmp <- asc_hh$AGa_AgriPlots %>% # land
  dplyr::select(IDNO,AGa_0) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(AGa_0 = ifelse(AGa_0=="Yes",1,0)) %>% # recode
  right_join(res,by="IDNO")
tmp <- asc_hh$AGe_Livestock %>% # land
  dplyr::select(IDNO,AGe_1) %>% # livestock
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(AGe_1 = ifelse(AGe_1=="Yes",1,0)) %>% # recode
  right_join(tmp,by="IDNO")
tmp <- asc_hh$L_DurableGoods %>% # boats
  dplyr::select(IDNO,DurableGoodID,l_1) %>%
  filter(DurableGoodID %in% # keep rows applying relevant goods
           unique(DurableGoodID)[c(20:23)]) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(DurableGoodID,l_1) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(bt=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(bt=sum(bt,na.rm=T)) %>% # summarise for HH
  mutate(bt=ifelse(bt>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  right_join(tmp,by="IDNO")  # add to other cols
tmp$lv_pas <- ifelse(rowSums(tmp[-1],na.rm=T)>0,1,0) # using base R because dplyr not working for some reason

hwb_tmp <- tmp %>% # bind
  dplyr::select(IDNO,lv_pas) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## RISK
# rk_exp
# Experienced two shocks in the last year
hwb_tmp <- asc_hh$R_WellbeingShockRoster%>%
  dplyr::select(IDNO,Shock_ID, r_20_a) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(Shock_ID, r_20_a) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(rk_exp=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(rk_exp=sum(rk_exp,na.rm=T)) %>% # summarise for HH
  mutate(rk_exp=ifelse(rk_exp>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## SUBJECTIVE WELLBEING
# swb
hwb_tmp <- asc_hh$R_WellBeing %>%
  dplyr::select(IDNO,swb=r_12) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(swb= as.character(swb)) %>% # make character
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
 # codes
lvls(vrs)

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
hwb_tmp <- plyr::rbind.fill(asc_hh$AGb_AgriInputsRoster[c("IDNO","AGb_14_b")],      
           asc_hh$AGc_AgriSeedsRoster[c("IDNO","AGc_15_b")],
           asc_hh$AGe_LivestockRoster[c("IDNO","AGe_12")]) %>%
    mutate_all(funs(ifelse(is.na(.), 0, .))) %>% # NAs mean zero here
    mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
    mutate(rwb_cm_st=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>%  # get row sums
    group_by(IDNO) %>%
    summarise(rwb_cm_st=sum(rwb_cm_st,na.rm=T)) %>% # summarise for HH
    mutate(rwb_cm_st=ifelse(rwb_cm_st>0,1,0)) %>% # recode
    group_by(IDNO) %>% 
    filter(row_number()==1) %>%  
    full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Community agency
# rwb_cm_ag
# Disatissfied (or below) with friendships or community support
hwb_tmp <- asc_hh$R_WellBeing %>%
  dplyr::select(IDNO,rwb_cm_ag=r_9) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_cm_ag = ifelse(as.numeric(factor(rwb_cm_ag)) %in% c(2,5),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# No data
hwb_tmp <- asc_hh$R_WellBeing %>%
  dplyr::select(IDNO,rwb_fm_ag=r_2) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_fm_ag = ifelse(as.numeric(factor(rwb_fm_ag)) %in% c(2,5),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## c) Check variables and tidy  ###################################

# make values annual as needed
hwb_tmp <- hwb_tmp %>%
  group_by(hhid) %>%
  summarise(
    pj_hhid = as.character(getmode(IDNO)),
    pjnm = as.character(getmode(pjnm)),
    cn = as.character(getmode(cn)),
    yr = getmode(yr),
    admn1 = as.character(getmode(admn1)),
    admn2 = as.character(getmode(admn2)),
    admn3 = as.character(getmode(admn3)),
    admn4 = as.character(getmode(admn4)),
    admn1n = as.character(getmode(admn1)), # admin division number codes
    admn2n = as.character(getmode(admn2)), 
    admn3n = as.character(getmode(admn3)), 
    admn4n = as.character(getmode(admn4)), 
    ses = as.character(getmode(ses)),
    gnd = as.character(getmode(gnd)),
    rsp_age = getmode(rsp_age),
    edu_yrs = trunc(median(edu_yrs,na.rm=T)), 
    edu_chld_att = trunc(median(edu_chld_att,na.rm=T)),
    hlt_chld_mt = trunc(median(hlt_chld_mt,na.rm=T)),
    hlt_fd_sec = trunc(median(hlt_fd_sec, na.rm=T)),
    hlt_pt = trunc(median(hlt_pt, na.rm=T)),
    ls_elec = trunc(median(ls_san, na.rm=T)),
    ls_san = trunc(median(ls_san, na.rm=T)),
    ls_wat = trunc(median(ls_wat, na.rm=T)),
    ls_hse = trunc(median(ls_hse, na.rm=T)),
    ls_fuel = trunc(median(ls_fuel, na.rm=T)),
    ls_ast = trunc(median(ls_ast, na.rm=T)),
    lv_pas = trunc(median(lv_pas, na.rm=T)),
    rk_exp = trunc(median(lv_pas, na.rm=T)),
    swb = as.character(getmode(swb)),
    rwb_cm_st = trunc(median(rwb_cm_st, na.rm=T)),
    rwb_cm_ag = trunc(median(rwb_cm_ag, na.rm=T)),
    rwb_fm_st = trunc(median(rwb_fm_st, na.rm=T)),
    rwb_fm_ag = trunc(median(rwb_fm_ag, na.rm=T))
  )
hwb_tmp$hhid <- NULL

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)] 

# check col classes before merge
sapply(hwb_tmp,class)

# remove wave from hhid
hwb_tmp$pj_hhid <- substring(hwb_tmp$pj_hhid,3)

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(asc_hh,hwb_tmp,wv1,wv2,vrs,tmp)

```

**11. ASSETS - PERU **
```{r assets, message = FALSE, warning = FALSE}

#### a) get all data csvs in list object  #####################
# ASSETS did surveys in two rounds. To save on code, for each survey section, I combine the csv into one dataframe with a unique response id (wave + hh id). Values for 
# each wave can be seperated or aggregated later as needed

nm1 <- list.files("../data/raw/assets_peru_initial_unpublished/Peru/Wave1/CSV",
                  pattern="*.csv",full.names=T)
nm2 <- list.files("../data/raw/assets_peru_initial_unpublished/Peru/Wave2/CSV",
                  pattern="*.csv",full.names=T)
asp_hh <- list()
for (i in 1:length(nm1)){
  wv1 <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nm1[i])
  wv1$wv <- 1 # wave number
  wv1$IDNO <- paste(wv1$wv,wv1$Pueblo, 
                    wv1$Hogar,sep="_") # unique response ID
  wv2 <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nm2[i])
  names(wv2) <- gsub( "W2", "", names(wv2)) # fix wv2 names
  wv2$wv <- 2 # wave number
  wv2$IDNO <- paste(wv2$wv,wv2$Pueblo, 
                    wv2$Hogar,sep="_") # unique response ID
  asp_hh[[i]] <- plyr::rbind.fill(wv1,wv2)
  names(asp_hh)[i] <- strsplit(nm1[i],"/")[[1]][8]
  names(asp_hh)[i] <- paste0(strsplit(names(asp_hh)[i],"_")[[1]][c(3,5)],collapse="_")
  names(asp_hh)[i] <- stringr::str_sub(names(asp_hh)[i],1,-5)
  
  # convert NAs
  asp_hh[[i]][asp_hh[[i]]==""] <- NA
  asp_hh[[i]][asp_hh[[i]]=="-999"] <- NA
  asp_hh[[i]][asp_hh[[i]]=="-998"] <- NA
  asp_hh[[i]][asp_hh[[i]]=="-997"] <- NA
  asp_hh[[i]][asp_hh[[i]]=="-888"] <- NA
  asp_hh[[i]]$hhid <- paste(asp_hh[[i]]$Pueblo, # add hhid
                            asp_hh[[i]]$Hogar, sep="_")
}

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS
hwb_tmp <- data.frame(stringsAsFactors = F,
  IDNO = asp_hh$A_InterviewDetails$IDNO, # wave number + hogar
  hhid = asp_hh$A_InterviewDetails$Hogar, # for aggregating later. then remove
  pjnm = "asp",
  cn = as.character("PER"),
  yr = 2014,
  admn1 = as.character(NA), # to add name from spatial data
  admn2 = as.character(NA), # to add name from spatial data
  admn3 = as.character(NA),
  admn4 = asp_hh$A_InterviewDetails$Pueblo,
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = NA, 
  ses = as.character(NA) # to add name from spatial data
)

hwb_tmp <- asp_hh$B_Roster %>%
  dplyr::select(IDNO,gnd=b_2,rsp_age=b_5_b) %>%
  group_by(IDNO) %>%
  filter(row_number()==1) %>%
  mutate(rsp_age= 2014-rsp_age) %>%
  full_join(hwb_tmp,.)

hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("male","female"))) # add names to gender

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- full_join(asp_hh$B_Roster[,c("IDNO","HHMemberID","b_5_b")],asp_hh$C_Education[,c("IDNO","HHMemberID","c_6")], 
                     by = c("IDNO","HHMemberID")) %>%
  { . ->> vrs } %>%  # keep vars
  mutate(age=2014-b_5_b,edu=as.numeric(factor(c_6))) %>% 
  group_by(IDNO) %>%
  summarise(edu_yrs = ifelse(length(age[edu %in% c(4,11:18)]>=10)>0,1,0)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# edu_chld_att
# Any school-aged child is not attending school for at least six years
hwb_tmp <- full_join(asp_hh$B_Roster[,c("IDNO","HHMemberID","b_5_b")],asp_hh$C_Education[,c("IDNO","HHMemberID","c_8")], 
                     by = c("IDNO","HHMemberID")) %>%
  { . ->> vrs } %>%  # keep vars
  mutate(age=2014-b_5_b,edu=as.numeric(factor(c_8))) %>%
  group_by(IDNO)  %>% 
  summarise(edu_chld_att = ifelse(length(age[edu %in% c(1)]<=12)>0,1,0)) %>%  # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## HEALTH

# hlt_chld_mt
#  Alternative 1: has any child below 5 years died in the last year
hwb_tmp <- asp_hh$E_Maternity %>%
  dplyr::select(IDNO,hlt_chld_mt=e_8) %>%
  { . ->> vrs } %>% # keep vars
  mutate(hlt_chld_mt= as.numeric(factor(hlt_chld_mt))) %>%
  group_by(IDNO) %>%
  summarise(hlt_chld_mt=ifelse(c(2) %in% hlt_chld_mt,0,1)) %>% # assuming NA is No
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_fd_sec
# Reported not having enough to eat in the last 12 months
hwb_tmp <- asp_hh$J_FoodSecurity %>%
  dplyr::select(IDNO,j_1_c:j_1_d) %>%
  { . ->> vrs } %>% # keep vars
    mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(hlt_fd_sec=ifelse(rowSums(dplyr::select(.,-IDNO),na.rm=T)>0,0,1)) %>%
  dplyr::select(IDNO,hlt_fd_sec) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_pt
# Did not eat meat in last week, or every week on average over period
pt <- delta_locs <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,
                       "../data/proc/initial/asm_protein_list.csv")
hwb_tmp <- asp_hh$I_FoodRoster %>%
  dplyr::select(IDNO,FoodID,i_2) %>%
  filter(FoodID %in% # keep rows applying to meat
           unique(FoodID)[pt$X[pt$meat==1]]) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(FoodID,i_2) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(hlt_pt=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(hlt_pt=sum(hlt_pt,na.rm=T)) %>% # summarise for HH
  mutate(hlt_pt=ifelse(hlt_pt>0,1,0)) %>% # recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVING STANDARDS

# ls_elec
# no data
hwb_tmp <- asp_hh$H_Housing %>%
  dplyr::select(IDNO,ls_elec=h_20) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_elec = ifelse(ls_elec=="No",0,1)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_san
# The household’s sanitation facility is not flush toilet or latrine, or ventilated improved pit or composting toilet
hwb_tmp <- asp_hh$H_Housing %>%
  dplyr::select(IDNO, ls_san=h_32) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_san = as.numeric(factor(ls_san))) %>% # make numeric code
  mutate(ls_san = ifelse(ls_san %in% c(1,2),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_wat
# Is not piped water, public tap, borehole or pump, protected well, protected spring or rainwater
hwb_tmp <- asp_hh$H_Housing %>%
  dplyr::select(IDNO, ls_wat=h_25) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_wat = as.numeric(factor(ls_wat))) %>%  # make numeric code
  mutate(ls_wat = ifelse(ls_wat %in% c(1,2,7,20,21),0,1)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_hse
# At least one of the three housing materials for roof, walls and floor are inadequate: the floor is of natural materials and/or the roof and/or walls are of natural or rudimentary materials
hwb_tmp <- asp_hh$H_Housing %>%
  dplyr::select(IDNO, wl=h_5, rf= h_6, fl= h_7)  %>%
  { . ->> vrs }  %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))))   %>% 
  mutate(wl = ifelse(wl %in% c(3,6),1,0))  %>% # recode underlying vats
  mutate(rf = ifelse(rf %in% c(1),1,0)) %>%
  mutate(fl= ifelse(fl %in% c(1,7,8),1,0)) %>%
  mutate(ls_hse = ifelse(rowSums(dplyr::select(.,-IDNO))<2,0,1)) %>% # make var
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  dplyr::select(IDNO,ls_hse) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# ls_fuel
# The household cooks with dung or wood
hwb_tmp <- asp_hh$H_Housing %>%
  dplyr::select(IDNO,ls_fuel=h_9) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_fuel=as.numeric(factor(ls_fuel))) %>% # make numeric code
  mutate(ls_fuel=ifelse(ls_fuel %in% c(2,3,5),0,1)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_ast
# The household does not own more than one of the following items: radio, TV, telephone, bike, motorbike computer, or refrigerator (conditional on not owning a car or truck). Or similar assets in each survey.
hwb_tmp <- asp_hh$L_DurableGoods %>%
  dplyr::select(IDNO,DurableGoodID,l_1) %>%
  filter(DurableGoodID %in% # keep rows applying relevant goods
           unique(DurableGoodID)[c(1,2,16,19,25,26)]) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(DurableGoodID,l_1) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(ls_ast=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(ls_ast=sum(ls_ast,na.rm=T)) %>% # summarise for HH
  mutate(ls_ast=ifelse(ls_ast>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: > 1ha agricultural land; fishing vessel; livestock

res <- hwb_tmp[1]
tmp <- asp_hh$AGa_AgriPlots %>% # land
  dplyr::select(IDNO,AGa_0) %>%
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(AGa_0 = ifelse(AGa_0=="Yes",1,0)) %>% # recode
  right_join(res,by="IDNO")
tmp <- asp_hh$AGe_Livestock %>% # land
  dplyr::select(IDNO,AGe_1) %>% # livestock
  drop_na() %>%
  { . ->> vrs } %>% # keep vars
  mutate(AGe_1 = ifelse(AGe_1=="Yes",1,0)) %>% # recode
  right_join(tmp,by="IDNO")
tmp <- asp_hh$L_DurableGoods %>% # boats
  dplyr::select(IDNO,DurableGoodID,l_1) %>%
  filter(DurableGoodID %in% # keep rows applying relevant goods
           unique(DurableGoodID)[c(20:23)]) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(DurableGoodID,l_1) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(bt=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(bt=sum(bt,na.rm=T)) %>% # summarise for HH
  mutate(bt=ifelse(bt>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  right_join(tmp,by="IDNO")  # add to other cols
tmp$lv_pas <- ifelse(rowSums(tmp[-1],na.rm=T)>0,1,0) # using base R because dplyr not working for some reason

hwb_tmp <- tmp %>% # bind
  dplyr::select(IDNO,lv_pas) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## RISK
# rk_exp
# Experienced two shocks in the last year
hwb_tmp <- asp_hh$R_Wellb%>%
  dplyr::select(IDNO,Shock_ID, r_20_a) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(Shock_ID, r_20_a) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(rk_exp=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(rk_exp=sum(rk_exp,na.rm=T)) %>% # summarise for HH
  mutate(rk_exp=ifelse(rk_exp>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## SUBJECTIVE WELLBEING
# swb
hwb_tmp <- asp_hh$R_Wellbeing %>%
  dplyr::select(IDNO,swb=r_12) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(swb= as.character(swb)) %>% # make character
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
 # codes
lvls(vrs)

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
hwb_tmp <- plyr::rbind.fill(asp_hh$AGb_AgriInputsRoster[c("IDNO","AGb_14_b")],      
           asp_hh$AGc_AgriSeedsRoster[c("IDNO","AGc_15_b")],
           asp_hh$AGe_LivestockRoster[c("IDNO","AGe_12")]) %>%
    mutate_all(funs(ifelse(is.na(.), 0, .))) %>% # NAs mean zero here
    mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
    mutate(rwb_cm_st=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>%  # get row sums
    group_by(IDNO) %>%
    summarise(rwb_cm_st=sum(rwb_cm_st,na.rm=T)) %>% # summarise for HH
    mutate(rwb_cm_st=ifelse(rwb_cm_st>0,1,0)) %>% # recode
    group_by(IDNO) %>% 
    filter(row_number()==1) %>%  
    full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Community agency
# rwb_cm_ag
# Disatissfied (or below) with friendships or community support
hwb_tmp <- asp_hh$R_Wellbeing %>%
  dplyr::select(IDNO,rwb_cm_ag=r_9) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_cm_ag = ifelse(as.numeric(factor(rwb_cm_ag)) %in% c(2,5),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# No data
hwb_tmp <- asp_hh$R_Wellbeing %>%
  dplyr::select(IDNO,rwb_fm_ag=r_2) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_fm_ag = ifelse(as.numeric(factor(rwb_fm_ag)) %in% c(2,5),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## c) Check variables and tidy  ###################################

# make values annual as needed
hwb_tmp <- hwb_tmp %>%
  group_by(hhid) %>%
  summarise(
    pj_hhid = as.character(getmode(IDNO)),
    pjnm = as.character(getmode(pjnm)),
    cn = as.character(getmode(cn)),
    yr = getmode(yr),
    admn1 = as.character(getmode(admn1)),
    admn2 = as.character(getmode(admn2)),
    admn3 = as.character(getmode(admn3)),
    admn4 = as.character(getmode(admn4)),
    admn1n = as.character(getmode(admn1)), # admin division number codes
    admn2n = as.character(getmode(admn2)), 
    admn3n = as.character(getmode(admn3)), 
    admn4n = as.character(getmode(admn4)), 
    ses = as.character(getmode(ses)),
    gnd = as.character(getmode(gnd)),
    rsp_age = getmode(rsp_age),
    edu_yrs = trunc(median(edu_yrs,na.rm=T)), 
    edu_chld_att = trunc(median(edu_chld_att,na.rm=T)),
    hlt_chld_mt = trunc(median(hlt_chld_mt,na.rm=T)),
    hlt_fd_sec = trunc(median(hlt_fd_sec, na.rm=T)),
    hlt_pt = trunc(median(hlt_pt, na.rm=T)),
    ls_elec = trunc(median(ls_san, na.rm=T)),
    ls_san = trunc(median(ls_san, na.rm=T)),
    ls_wat = trunc(median(ls_wat, na.rm=T)),
    ls_hse = trunc(median(ls_hse, na.rm=T)),
    ls_fuel = trunc(median(ls_fuel, na.rm=T)),
    ls_ast = trunc(median(ls_ast, na.rm=T)),
    lv_pas = trunc(median(lv_pas, na.rm=T)),
    rk_exp = trunc(median(lv_pas, na.rm=T)),
    swb = as.character(getmode(swb)),
    rwb_cm_st = trunc(median(rwb_cm_st, na.rm=T)),
    rwb_cm_ag = trunc(median(rwb_cm_ag, na.rm=T)),
    rwb_fm_st = trunc(median(rwb_fm_st, na.rm=T)),
    rwb_fm_ag = trunc(median(rwb_fm_ag, na.rm=T))
  )
hwb_tmp$hhid <- NULL

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)] 

# check col classes before merge
sapply(hwb_tmp,class)

# remove wave from hhid
hwb_tmp$pj_hhid <- substring(hwb_tmp$pj_hhid,3)

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(asp_hh,hwb_tmp,wv1,wv2,vrs,tmp)

```

**12. ASSETS - MALAWI **
```{r assets, message = FALSE, warning = FALSE}

#### a) get all data csvs in list object  #####################
# ASSETS did surveys in two rounds. To save on code, for each survey section, I combine the csv into one dataframe with a unique response id (wave + hh id). Values for 
# each wave can be seperated or aggregated later as needed
nm1 <- list.files("../data/raw/assets_malawi_initial_unpublished/Wave1",
                  pattern="*.csv",full.names=T)
nm2 <- list.files("../data/raw/assets_malawi_initial_unpublished/Wave2",
                  pattern="*.csv",full.names=T)
asm_hh <- list()
for (i in 1:length(nm1)){
  wv1 <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nm1[i])
  wv1$wv <- 1 # wave number
  wv1$IDNO <- paste(wv1$wv,wv1$FINALCODE,sep="_") # unique response ID
  wv2 <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nm2[i])
  names(wv2) <- gsub( "W2", "", names(wv2)) # fix wv2 names
  wv2$wv <- 2 # wave number
  wv2$IDNO <- paste(wv2$wv,wv2$Hogar,sep="_") # unique response ID
  asm_hh[[i]] <- plyr::rbind.fill(wv1,wv2)
  names(asm_hh)[i] <- strsplit(nm1[i],"/")[[1]][6]
  names(asm_hh)[i] <- paste0(strsplit(names(asm_hh)[i],"_")[[1]][4],collapse="_")
  names(asm_hh)[i] <- stringr::str_sub(names(asm_hh)[i],1,-5)
  
  # convert NAs
  asm_hh[[i]][asm_hh[[i]]==""] <- NA
  asm_hh[[i]][asm_hh[[i]]=="-999"] <- NA
  asm_hh[[i]][asm_hh[[i]]=="-998"] <- NA
  asm_hh[[i]][asm_hh[[i]]=="-997"] <- NA
  asm_hh[[i]][asm_hh[[i]]=="-888"] <- NA
  # asm_hh[[i]]$hhid <- paste(asm_hh[[i]]$Pueblo, # add hhid
  #                           asm_hh[[i]]$Hogar, sep="_")
}

# make ID look up table for aggregation
# tmp <- asm_hh$HHRoster %>%
#   dplyr::select(sett_nm2 = Village, sett_nm1 = Pueblo, pj_hhid = IDNO) %>%
#   mutate(pj_hhid = gsub(".*_","",pj_hhid)) %>%
#   mutate(sett_nm = dplyr::coalesce(sett_nm1,sett_nm2)) %>%
#   mutate(sett_pjid = sett_nm) %>%
#   dplyr::select(-sett_nm1,-sett_nm2) %>%
#   unique()
# write.csv(tmp,"asm_hhid.csv")

# add extra dataframes not included in above
nmex <- list.files("../data/raw/assets_malawi_initial_unpublished/Wave1/extra",
                  pattern="*.csv",full.names=T)
for (i in 1:length(nmex)){
  wv1 <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,nmex[i])
  wv1$wv <- 1 # wave number
  wv1$IDNO <- paste(wv1$wv,wv1$FINALCODE,sep="_") # unique response ID
  asm_hh[[length(asm_hh)+1]] <- plyr::rbind.fill(wv1,wv2)
  names(asm_hh)[length(asm_hh)] <- strsplit(nmex[i],"/")[[1]][7]
  names(asm_hh)[length(asm_hh)] <- paste0(strsplit(names(asm_hh)[length(asm_hh)],"_")[[1]][4],collapse="_")
  names(asm_hh)[length(asm_hh)] <- stringr::str_sub(names(asm_hh)[length(asm_hh)],1,-5)
  asm_hh[[length(asm_hh)]][asm_hh[[length(asm_hh)]]==""] <- NA
  asm_hh[[length(asm_hh)]][asm_hh[[length(asm_hh)]]=="-999"] <- NA
  asm_hh[[length(asm_hh)]][asm_hh[[length(asm_hh)]]=="-998"] <- NA
  asm_hh[[length(asm_hh)]][asm_hh[[length(asm_hh)]]=="-997"] <- NA
  asm_hh[[length(asm_hh)]][asm_hh[[length(asm_hh)]]=="-888"] <- NA
}

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS

tmp <- unique(asm_hh$HHRoster[c("Village", "IDNO", "FINALCODE","Hogar")])
tmp <- tmp %>%
  mutate(hhid = dplyr::coalesce(tmp$FINALCODE, tmp$Hogar))

hwb_tmp <- data.frame(stringsAsFactors = F,
  IDNO = tmp$IDNO, # wave number + hogar
  hhid = tmp$hhid, # for aggregating later. then remove
  pjnm = "asm",
  cn = as.character("MWI"),
  yr = 2014,
  admn1 = as.character(NA), # to add name from spatial data
  admn2 = as.character(NA), # to add name from spatial data
  admn3 = as.character(NA),
  admn4 = tmp$Village,
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = NA, 
  ses = as.character(NA) # to add name from spatial data
)

hwb_tmp <- asm_hh$HHRoster %>%
  dplyr::select(IDNO,gnd=b_2,rsp_age=b_5_b) %>%
  group_by(IDNO) %>%
  filter(row_number()==1) %>%
  mutate(rsp_age= 2014-rsp_age) %>%
  full_join(hwb_tmp,.)

hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("male","female"))) # add names to gender

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- full_join(asm_hh$HHRoster[,c("IDNO","HHMemberID","b_5_b")],asm_hh$HHEducation[,c("IDNO","HHMemberID","c_6")], 
                     by = c("IDNO","HHMemberID")) %>%
  { . ->> vrs } %>%  # keep vars
  mutate(age=2014-b_5_b,edu=as.numeric(factor(c_6))) %>% 
  group_by(IDNO) %>%
  summarise(edu_yrs = ifelse(length(age[edu %in% c(8:16)]>=10)>0,1,0)) %>% # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# edu_chld_att
# Any school-aged child is not attending school for at least six years
hwb_tmp <- full_join(asm_hh$HHRoster[,c("IDNO","HHMemberID","b_5_b")],asm_hh$HHEducation[,c("IDNO","HHMemberID","c_8")], 
                     by = c("IDNO","HHMemberID")) %>%
  { . ->> vrs } %>%  # keep vars
  mutate(age=2014-b_5_b,edu=as.numeric(factor(c_8))) %>%
  group_by(IDNO)  %>% 
  summarise(edu_chld_att = ifelse(length(age[edu %in% c(1)]<=12)>0,1,0)) %>%  # ifelse recode
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## HEALTH

# hlt_chld_mt
#  Alternative 1: has any child below 5 years died in the last year
hwb_tmp <- asm_hh$Maternity %>%
  dplyr::select(IDNO,hlt_chld_mt=e_8) %>%
  { . ->> vrs } %>% # keep vars
  mutate(hlt_chld_mt= as.numeric(factor(hlt_chld_mt))) %>%
  group_by(IDNO) %>%
  summarise(hlt_chld_mt=ifelse(c(2) %in% hlt_chld_mt,0,1)) %>% # assuming NA is No
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# hlt_fd_sec
# Reported not having enough to eat in the last 12 months
hwb_tmp <- asm_hh$FoodSecurity %>%
  dplyr::select(IDNO,j_1_c:j_1_d) %>%
  { . ->> vrs } %>% # keep vars
    mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(hlt_fd_sec=ifelse(rowSums(dplyr::select(.,-IDNO),na.rm=T)>0,0,1)) %>%
  dplyr::select(IDNO,hlt_fd_sec) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)


# hlt_pt
# Did not eat meat in last week, or every week on average over period
# pt <- delta_locs <- read.csv(encoding="UTF-8",stringsAsFactors = FALSE,
#                        "../data/proc/initial/asm_protein_list.csv")
hwb_tmp <- asm_hh$FoodMeat %>%
  dplyr::select(IDNO,MeatID,i_12) %>%
  group_by(IDNO) %>%
  summarise(hlt_pt = max(as.numeric(factor(i_12)))-1) %>%
  full_join(hwb_tmp,.)

## LIVING STANDARDS

# ls_elec
hwb_tmp <- asm_hh$Housing %>%
  dplyr::select(IDNO,ls_elec=h_20) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_elec = ifelse(ls_elec=="No",0,1)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_san
# The household’s sanitation facility is not flush toilet or latrine, or ventilated improved pit or composting toilet
hwb_tmp <- asm_hh$Housing %>%
  dplyr::select(IDNO, ls_san=h_32) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_san = as.numeric(factor(ls_san))) %>% # make numeric code
  mutate(ls_san = ifelse(ls_san %in% c(2,3),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_wat
# Is not piped water, public tap, borehole or pump, protected well, protected spring or rainwater
hwb_tmp <- asm_hh$Housing %>%
  dplyr::select(IDNO, ls_wat=h_25) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_wat = as.numeric(factor(ls_wat))) %>%  # make numeric code
  mutate(ls_wat = ifelse(ls_wat %in% c(4,11,12,13),0,1)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_hse
# At least one of the three housing materials for roof, walls and floor are inadequate: the floor is of natural materials and/or the roof and/or walls are of natural or rudimentary materials
hwb_tmp <- asm_hh$Housing %>%
  dplyr::select(IDNO, wl=h_5, rf= h_6, fl= h_7)  %>%
  { . ->> vrs }  %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))))   %>% 
  mutate(wl = ifelse(wl %in% c(1,2),1,0))  %>% # recode underlying vats
  mutate(rf = ifelse(rf %in% c(2),1,0)) %>%
  mutate(fl= ifelse(fl %in% c(1,5),1,0)) %>%
  mutate(ls_hse = ifelse(rowSums(dplyr::select(.,-IDNO))<2,0,1)) %>% # make var
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  dplyr::select(IDNO,ls_hse) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)
  
# ls_fuel
# The household cooks with dung or wood
hwb_tmp <- asm_hh$Housing %>%
  dplyr::select(IDNO,ls_fuel=h_9) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(ls_fuel=as.numeric(factor(ls_fuel))) %>% # make numeric code
  mutate(ls_fuel=ifelse(ls_fuel %in% c(2,3,4),0,1)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# ls_ast
# The household does not own more than one of the following items: radio, TV, telephone, bike, motorbike computer, or refrigerator (conditional on not owning a car or truck). Or similar assets in each survey.
hwb_tmp <- asm_hh$DurableGoods %>%
  dplyr::select(IDNO,DurableGoodID,l_1) %>%
  filter(DurableGoodID %in% # keep rows applying relevant goods
           unique(DurableGoodID)[c(19,17,18,12,11)]) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(DurableGoodID,l_1) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(ls_ast=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(ls_ast=sum(ls_ast,na.rm=T)) %>% # summarise for HH
  mutate(ls_ast=ifelse(ls_ast>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## LIVELIHOODS
# lv_pas
# The household does not own at least one of the following: > 1ha agricultural land; fishing vessel; livestock

res <- hwb_tmp[1]

tmp <- asm_hh$HHAgriPlotsRoster %>%
    mutate(IDNO,sett_pjid=Village) %>%
    dplyr::select(IDNO,sett_pjid,sz_init=AGa_2_a,un_init=AGa_2_b,ten=AGa_11) %>%
    # fix one variable
    mutate(un_init = replace(un_init, IDNO=="1_5a4138  ","Sq. meters")) %>%
    mutate(un = as.numeric(as.character( # convert to Ha
      factor(un_init,labels=c(2.4,1,1,1/10000))
    ))) %>%
    mutate(sz = sz_init * un) %>%
  filter(!(ten %in% c("Moved in without permission", "Short term rent",
                    "Borrowed for free)", "Leasehold", "Farming as tenant"))) %>%
  filter(sz < 1) %>%
  unique() %>%
  mutate(AGa_0 = 1) %>% # recode
  dplyr::select(IDNO,AGa_0) %>%
  right_join(res,by="IDNO") %>%
  mutate(AGa_0 = replace(AGa_0, which(is.na(AGa_0)),0))
tmp <- asm_hh$Livestock %>% # land
  dplyr::select(IDNO,GanadoID, AGe_2) %>% # livestock
  filter(GanadoID %in% c("Bull / Ox", "Cow", "Calf","Sheep","Donkey",
                         "Chicken Broiler", "Pigs", "Goats")) %>%
  filter(AGe_2 == "Yes") %>%
  dplyr::select(-GanadoID, -AGe_2) %>%
  unique() %>%
  mutate(AGe_1 = 1) %>% # recode
  right_join(res,by="IDNO") %>%
  mutate(AGe_1 = replace(AGe_1, which(is.na(AGe_1)),0)) %>% # recode
  right_join(tmp,by="IDNO")
tmp <- asm_hh$DurableGoods %>% 
  dplyr::select(IDNO,DurableGoodID,l_1) %>%
  filter(DurableGoodID %in% # keep rows applying relevant goods
           unique(DurableGoodID)[c(8:10)]) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(DurableGoodID,l_1) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(bt=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(bt=sum(bt,na.rm=T)) %>% # summarise for HH
  mutate(bt=ifelse(bt>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  right_join(tmp,by="IDNO")  # add to other cols
tmp$lv_pas <- ifelse(rowSums(tmp[-1],na.rm=T)>0,1,0) # using base R because dplyr not working for some reason

hwb_tmp <- tmp %>% # bind
  dplyr::select(IDNO,lv_pas) %>%
  full_join(hwb_tmp,.)

## RISK
# rk_exp
# Experienced two shocks in the last year
hwb_tmp <- asm_hh$Shocks %>%
  dplyr::select(IDNO,ShockID, r_20_a) %>%
  mutate(id=seq(1,nrow(.))) %>%
  spread(ShockID, r_20_a) %>%
  dplyr::select(-id) %>%
  { . ->> vrs } %>% # keep vars
  mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
  mutate(rk_exp=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>% # get row sums
  group_by(IDNO) %>%
  summarise(rk_exp=sum(rk_exp,na.rm=T)) %>% # summarise for HH
  mutate(rk_exp=ifelse(rk_exp>1,1,0)) %>% # recode
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## SUBJECTIVE WELLBEING
# swb
hwb_tmp <- asm_hh$HHWellBeing %>%
  dplyr::select(IDNO,swb=r_12) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(swb= as.character(swb)) %>% # make character
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
 # codes
lvls(vrs)

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
hwb_tmp <- plyr::rbind.fill(asm_hh$Inputs[c("IDNO","AGb_14_b")],      
           asm_hh$Seeds[c("IDNO","AGc_15_b")],
           asm_hh$Livestock[c("IDNO","AGe_12")]) %>%
    mutate_all(funs(ifelse(is.na(.), 0, .))) %>% # NAs mean zero here
    mutate_at(.vars=vars(-IDNO), # make underlying vars numeric zero based
            .funs=list(~ as.numeric(factor(.))-1)) %>% # recode
    mutate(rwb_cm_st=rowSums(dplyr::select(.,-c(IDNO)),na.rm=T)) %>%  # get row sums
    group_by(IDNO) %>%
    summarise(rwb_cm_st=sum(rwb_cm_st,na.rm=T)) %>% # summarise for HH
    mutate(rwb_cm_st=ifelse(rwb_cm_st>0,1,0)) %>% # recode
    group_by(IDNO) %>% 
    filter(row_number()==1) %>%  
    full_join(hwb_tmp,.)


# Community agency
# rwb_cm_ag
# Disatissfied (or below) with friendships or community support
hwb_tmp <- asm_hh$HHWellBeing %>%
  dplyr::select(IDNO,rwb_cm_ag=r_9) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_cm_ag = ifelse(as.numeric(factor(rwb_cm_ag)) %in% c(2,5),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# No data
hwb_tmp <- asm_hh$HHWellBeing %>%
  dplyr::select(IDNO,rwb_fm_ag=r_2) %>%
  { . ->> vrs } %>% # keep vars
  drop_na() %>%
  mutate(rwb_fm_ag = ifelse(as.numeric(factor(rwb_fm_ag)) %in% c(2,5),0,1)) %>%
  group_by(IDNO) %>% 
  filter(row_number()==1) %>%
  full_join(hwb_tmp,.)
# codes
lvls(vrs)

## c) Check variables and tidy  ###################################

# make values annual as needed
hwb_tmp <- hwb_tmp %>%
  group_by(hhid) %>%
  summarise(
    pj_hhid = as.character(getmode(IDNO)),
    pjnm = as.character(getmode(pjnm)),
    cn = as.character(getmode(cn)),
    yr = getmode(yr),
    admn1 = as.character(getmode(admn1)),
    admn2 = as.character(getmode(admn2)),
    admn3 = as.character(getmode(admn3)),
    admn4 = as.character(getmode(admn4)),
    admn1n = as.character(getmode(admn1)), # admin division number codes
    admn2n = as.character(getmode(admn2)), 
    admn3n = as.character(getmode(admn3)), 
    admn4n = as.character(getmode(admn4)), 
    ses = as.character(getmode(ses)),
    gnd = as.character(getmode(gnd)),
    rsp_age = getmode(rsp_age),
    edu_yrs = trunc(median(edu_yrs,na.rm=T)), 
    edu_chld_att = trunc(median(edu_chld_att,na.rm=T)),
    hlt_chld_mt = trunc(median(hlt_chld_mt,na.rm=T)),
    hlt_fd_sec = trunc(median(hlt_fd_sec, na.rm=T)),
    hlt_pt = trunc(median(hlt_pt, na.rm=T)),
    ls_elec = trunc(median(ls_san, na.rm=T)),
    ls_san = trunc(median(ls_san, na.rm=T)),
    ls_wat = trunc(median(ls_wat, na.rm=T)),
    ls_hse = trunc(median(ls_hse, na.rm=T)),
    ls_fuel = trunc(median(ls_fuel, na.rm=T)),
    ls_ast = trunc(median(ls_ast, na.rm=T)),
    lv_pas = trunc(median(lv_pas, na.rm=T)),
    rk_exp = trunc(median(lv_pas, na.rm=T)),
    swb = as.character(getmode(swb)),
    rwb_cm_st = trunc(median(rwb_cm_st, na.rm=T)),
    rwb_cm_ag = trunc(median(rwb_cm_ag, na.rm=T)),
    rwb_fm_st = trunc(median(rwb_fm_st, na.rm=T)),
    rwb_fm_ag = trunc(median(rwb_fm_ag, na.rm=T))
  )
hwb_tmp$hhid <- NULL

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)] 

# check col classes before merge
sapply(hwb_tmp,class)

  # sort pj_hhid
  hwb_tmp$pj_hhid <- gsub(".*_","",hwb_tmp$pj_hhid)


# remove wave from hhid
# hwb_tmp$pj_hhid <- substring(hwb_tmp$pj_hhid,3)

# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(asm_hh,hwb_tmp,wv1,wv2,vrs,tmp)

```

**13. MIYUN**
```{r assets, message = FALSE, warning = FALSE}

#### a) get data #####################
require(haven)
miyun <- read_dta("C:/n4sdgs/r_analysis/data/raw/miyun/Miyun_Nat4SDGs.dta")
miyun <- miyun %>% mutate_if(is.factor,as.character)
miyun[miyun==-99] <- NA

miyun2 <- read_dta("C:/n4sdgs/r_analysis/data/raw/miyun/Miyun2015_ind.dta")
miyun2 <- miyun2 %>% mutate_if(is.factor,as.character)
miyun2[miyun2==-99] <- NA

miyun3 <- read_dta("C:/n4sdgs/r_analysis/data/raw/miyun/Miyun2015_hhwsums.dta")
miyun3 <- miyun3 %>% mutate_if(is.factor,as.character)
miyun3[miyun3==-99] <- NA

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS

hwb_tmp <- data.frame(stringsAsFactors = F,
  IDNO = as.character(miyun$hh_id), # wave number + hogar
  hh_id = as.character(miyun$hh_id),
  pjnm = "mi",
  cn = rep("mi",nrow(miyun)),
  yr = 2014,
  admn1 = as.character(NA), # to add name from spatial data
  admn2 = as.character(NA), # to add name from spatial data
  admn3 = as.character(NA),
  admn4 = as.character(NA),
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = miyun$vill_id, 
  ses = as.character(NA) # to add name from spatial data
)

hwb_tmp$gnd <- miyun$head_gend
hwb_tmp$rsp_age <- miyun$head_age
hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("male","female"))) # add names to gender

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- miyun %>%
  mutate(edu_yrs = ifelse(ed_max>=6,1,0)) %>% # ifelse recode
  dplyr::select(hh_id,edu_yrs) %>%
  full_join(hwb_tmp,.)

# edu_chld_att
# Any school-aged child is not attending school for at least six years
hwb_tmp <- miyun %>%
  mutate(edu_chld_att = ifelse(kidsinschool==0,0,1)) %>%
  mutate(edu_chld_att = ifelse(numkids==0,1,edu_chld_att)) %>%
  dplyr::select(hh_id, edu_chld_att) %>%
  full_join(hwb_tmp,.)

## HEALTH

# hlt_chld_mt
#  chronic illness in family
hwb_tmp <- miyun3 %>%
  mutate(hlt_chld_mt = ifelse(hh_health==2,0,1)) %>%
  dplyr::select(hh_id, hlt_chld_mt) %>%
  full_join(hwb_tmp,.)

# hlt_fd_sec
# HH in lowest quantile of food consumption
hwb_tmp <- miyun3 %>%
  select(hh_id,exp_food,hhsize) %>%
  drop_na() %>%
  mutate(hlt_fd_sec = exp_food/sqrt(hhsize)) %>%
  mutate(hlt_fd_sec = as.numeric(cut(hlt_fd_sec,breaks=quantile(hlt_fd_sec)))) %>%
  mutate(hlt_fd_sec = ifelse(hlt_fd_sec==1,0,1)) %>%
  full_join(hwb_tmp,.)

# hlt_pt
# no data
hwb_tmp$hlt_pt <- NA

## LIVING STANDARDS

# ls_elec
# no data
hwb_tmp$ls_elec <- NA

# ls_san
hwb_tmp <- miyun3 %>%
  select(hh_id,ls_san=sanitation) %>%
  drop_na() %>%
  mutate(ls_san = ifelse(ls_san==4,0,1)) %>%
  full_join(hwb_tmp,.)

# ls_wat
hwb_tmp <- miyun3 %>%
  select(hh_id,ls_wat=drinkwater) %>%
  drop_na() %>%
  mutate(ls_wat = ifelse(ls_wat%in%c(4,5),0,1)) %>%
  full_join(hwb_tmp,.)

# ls_hse
# no data
### UP TO HERE - COULD MAKE LOWER QUANTILE OF HOUSE AREA?
hwb_tmp$ls_hse <- NA

# ls_fuel
# no data
hwb_tmp$ls_fuel <- NA

# ls_ast
# data in survey form but not in data we have
hwb_tmp$ls_ast <- NA

## LIVELIHOODS
# data in survey form but not in data we have
hwb_tmp <- miyun3 %>%
  dplyr::select(hh_id,agland_tot,natforest_tot,econforest_tot) %>%
  mutate(lv_pas=rowSums(.[-1],na.rm=T)) %>%
  mutate(lv_pas=ifelse(lv_pas>0,1,0)) %>%
  dplyr::select(hh_id,lv_pas) %>%
  full_join(hwb_tmp,.)

## RISK
# rk_exp
# household reported borrowing from loan shark
hwb_tmp <- miyun3 %>%
  select(hh_id,rk_exp=loanshark) %>%
  mutate(rk_exp=ifelse(rk_exp<2,0,1)) %>%
  mutate(rk_exp=replace(rk_exp,is.na(rk_exp),1)) %>%
  full_join(hwb_tmp,.)

## SUBJECTIVE WELLBEING
# no data
hwb_tmp$swb <- NA

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
# data in survey form but not in data we have
hwb_tmp <- miyun3 %>%
  select(hh_id,cadre_familymemb,cadre_relative) %>%
  mutate(rwb_cm_st = ifelse(
    rowSums(dplyr::select(.,cadre_familymemb,cadre_relative),na.rm=T)>0,1,0)) %>%
  full_join(hwb_tmp,.)

# Community agency
# rwb_cm_ag
# data in survey form but not in data we have
hwb_tmp$rwb_cm_ag <- NA

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# No data
hwb_tmp$rwb_fm_ag <- as.numeric(NA) # no data

## c) Check variables and tidy  ###################################

hwb_tmp$hhid <- NULL

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)

names(hwb_tmp)[names(hwb_tmp)=="hh_id"] <- "pj_hhid"
hwb_tmp$IDNO <- NULL

# align col order with main df
hwb_tmp <- hwb_tmp[names(hwb_all)] 

# check col classes before merge
sapply(hwb_tmp,class)


# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_tmp$admn4n <- as.character(hwb_tmp$admn4n)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(miyun,hwb_tmp)

```

**14. ORISSA**
```{r assets, message = FALSE, warning = FALSE}

#### a) get data #####################
require(foreign)
#### a) get all data in list object  #####################

nm1 <- list.files("../data/raw/orissa_unpublished",
                  pattern="*.dta",full.names=T)
od_hh <- list()
for (i in 1:length(nm1)){
  tp <- read.dta(nm1[i])
  od_hh[[i]] <- tp
  names(od_hh)[i] <- strsplit(nm1[i],"/")[[1]][5]
  names(od_hh)[i] <- stringr::str_sub(names(od_hh)[i],1,-5)
  # convert NAs
  # asp_hh[[i]][asp_hh[[i]]==""] <- NA
  # asp_hh[[i]][asp_hh[[i]]=="-999"] <- NA
  # asp_hh[[i]][asp_hh[[i]]=="-998"] <- NA
  # asp_hh[[i]][asp_hh[[i]]=="-997"] <- NA
  # asp_hh[[i]][asp_hh[[i]]=="-888"] <- NA
  # asp_hh[[i]]$hhid <- paste(asp_hh[[i]]$Pueblo, # add hhid
  #                           asp_hh[[i]]$Hogar, sep="_")
}

od_hh$C.Land_Odisha$Site_code <- # align site ID data types 
  factor(od_hh$C.Land_Odisha$Site_code, 
         labels=levels(od_hh$A.hh_roaster_Odisha$Site_code))

## b) generate data in temporary dataframe  ###################################

## ID VARIABLES AND DEMOGRAPHICS

hwb_tmp <- data.frame(stringsAsFactors = F,
  Vil_HH_Code = od_hh$A.hh_roaster_Odisha$Vil_HH_Code,
  pj_hhid = as.character(od_hh$A.hh_roaster_Odisha$Vil_HH_Code),
  pjnm = "od",
  cn = "IND",
  yr = 2014,
  admn1 = as.character(NA), # to add name from spatial data
  admn2 = as.character(NA), # to add name from spatial data
  admn3 = as.character(NA),
  admn4 = as.character(od_hh$A.hh_roaster_Odisha$Site_code),
  admn1n = NA, # admin division number codes
  admn2n = NA, 
  admn3n = NA, 
  admn4n = NA, 
  ses = as.character(NA) # to add name from spatial data
)

hwb_tmp$gnd <- od_hh$A.hh_roaster_Odisha$Sex
hwb_tmp$rsp_age <- od_hh$A.hh_roaster_Odisha$Age
hwb_tmp$gnd <- as.character(factor(hwb_tmp$gnd,labels=c("male","female"))) # add names to gender

## EDUCATION 

# edu_yrs
# No household member aged 10 years or older has completed six years of schooling
hwb_tmp <- od_hh$A.hh_roaster_Odisha %>%
  mutate(edu_yrs = ifelse(Edu>=2,1,0)) %>% # ifelse recode
  dplyr::select(edu_yrs) %>%
  bind_cols(hwb_tmp,.)

# edu_chld_att
# data in survey form but not in data we have
hwb_tmp$edu_chld_att <- NA

## HEALTH

# hlt_chld_mt
#  no data
hwb_tmp$hlt_chld_mt <- NA

# hlt_fd_sec
# no data
hwb_tmp$hlt_fd_sec <- NA


# hlt_pt
# no data
hwb_tmp$hlt_pt <- NA

## LIVING STANDARDS

# ls_elec
# no data
hwb_tmp$ls_elec <- NA

# ls_san
# data in survey form but not in data we have
hwb_tmp$ls_san <- NA

# ls_wat
# data in survey form but not in data we have
hwb_tmp$ls_wat <- NA

# ls_hse
# Katcha is rudimentary
hwb_tmp <- od_hh$B.Asset_Odisha %>%
  dplyr::select(Assets3) %>%
  mutate(ls_hse = ifelse(Assets3=="katcha" ,0,1)) %>%
  dplyr::select(ls_hse) %>%
  bind_cols(hwb_tmp,.)

# ls_fuel
# no data
hwb_tmp$ls_fuel <- NA

# ls_ast
# Has TV, motorbike
hwb_tmp <- od_hh$B.Asset_Odisha %>%
  dplyr::select(Assets1, Asset4) %>%
  mutate_all(~as.numeric(.)-1) %>%
  mutate(ls_ast = ifelse(rowSums(dplyr::select(.,Assets1,Asset4),na.rm=T)>0,1,0)) %>%
  dplyr::select(ls_ast) %>%
  bind_cols(hwb_tmp,.)
  
## LIVELIHOODS
# lv_pas
# owns land
hwb_tmp <- od_hh$C.Land_Odisha %>%
  dplyr::select(starts_with("OL")) %>% 
mutate(lv_pas = ifelse(rowSums(dplyr::select(.,starts_with("OL")),na.rm=T)>0,1,0)) %>%
  dplyr::select(lv_pas) %>%
  bind_cols(hwb_tmp,.)

## RISK
# rk_exp
# no data
hwb_tmp$rk_exp <- NA

## SUBJECTIVE WELLBEING
# no data
hwb_tmp$swb <- NA

## RELATIONAL WELLBEING

# Community Opportunity Structures
# Household is not a member of, or has not received assistance from, one of the organisations or groups asked about in the survey
# rwb_cm_st
# data in survey form but not in data we have
hwb_tmp$rwb_cm_st <- NA


# Community agency
# rwb_cm_ag
# data in survey form but not in data we have
hwb_tmp$rwb_cm_ag <- NA

# Family opportunity structures
# rwb_fm_st
# No data
hwb_tmp$rwb_fm_st <- as.numeric(NA) # no data

# Family agency
# rwb_fm_ag
# No data
hwb_tmp$rwb_fm_ag <- as.numeric(NA) # no data

## c) Check variables and tidy  ###################################

hwb_tmp$Vil_HH_Code <- NULL

# check vars
summary(hwb_tmp)
hist_grid(hwb_tmp)


# align col order with main df
#hwb_tmp <- hwb_tmp[names(hwb_all)] 

# check col classes before merge
sapply(hwb_tmp,class)


# bind to main dataframe
hwb_tmp$swb <- as.character(hwb_tmp$swb)
hwb_tmp$admn4n <- as.character(hwb_tmp$admn4n)
hwb_all <- bind_rows(hwb_all,hwb_tmp)

# clear workspace
rm(miyun,hwb_tmp)


```

**Add IDs and spatial info**
```{r add, message = FALSE, warning = FALSE, include = TRUE}
#asp, asm, or, mi

### deal with NA
hwb_all <- hwb_all[which(!is.na(hwb_all$pjnm)),]

#### add N4S HH
hwb_all$hhid <- seq(1,nrow(hwb_all)) # N4S hh id


```

```{r final stuff, message = FALSE, warning = FALSE, include = TRUE}

## add provisioing means variables
pm_dat <- read.csv("../data/proc/prov_means_all.csv")
pm_dat$X <- NULL

hwb_all <- hwb_all %>%
  left_join(pm_dat,by=c("pjnm","pj_hhid","admn4","admn4n"))

### save data
# sort names

# hwb_all
write.csv(hwb_all,"../data/proc/hwb_all.csv")



```
